---
title: "Guideline for Contributing to NEPSroutines"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(eval = FALSE)
```

## Introduction

This file is a guideline for everyone developing and maintaining the NEPSroutines package. It explains the required workflow to implement changes using branches and to create a new package release on GitHub.

## Roles and Contributors

At the moment, all contributors in the GitHub project belong to one of two roles. However, this may change when the project is moved to the GitHub page of the scaling team.

-   **Maintainer**: The person who "owns" the project. Currently, this is `j-welling`. This is the only person who can bypass branch protection rules (see section *Branches*).

-   **Contributor**: Every other person who is part of the GitHub project.

*Here we could also add rules on who may be added as contributor.*

## Branching Workflow

This section describes the workflow of implementing changes to the package.

### Branches

The `main` branch represents the current state of the package. It is protected by the following **protection rules**:

1.  Changes can only be incorporated by opening a pull request.

2.  The pull request needs to be reviewed and approved by at least one other person.

3.  Only the maintainer can bypass these rules.

Changes are implemented using **extra branches**. Please use the following workflow:

-   Before starting to work on a new branch, **pull** the newest version of the main branch on your local repository.

-   Then **create a new branch** with a meaningful name (e.g., `add-new-feature`). Branches can be further divided into the three categories feature (new feature for users), bugfix, and chore (package maintenance). The category can be added to the branch name, e.g. `feature/add-this-feature`, `bugfix/fix-this-bug`, `chore/add-this-file`.

-   To improve clarity and traceability, it is recommended to create a new branch for every working package or feature.

You can pull the newest `main` version and create new branches by using the git GUI in R Studio or by writing these commands in the terminal:

```{bash}
# switch to main branch and pull newest version
git switch main
git pull
# create new branch
git switch -c my-new-branch-name
```

### Commits

Make small, logical commits. Each commit should represent one coherent change. The description should explain the changes in a short and precise way using present tense. No version numbers are required.

You can commit changes by using the git GUI in R Studio or by writing these commands in the terminal:

```{bash}
git commit # opens text editor to enter commit message manually
git commit -m "Add my new feature" # incorporates the commit message in the command
```

### Checks and Push

When all changes are implemented and committed, please verify if

-   the code is correct and does what it is supposed to do,

-   the documentation (including vignettes) is up to date, and

-   all checks and tests pass.

You can use the following commands:

```{r}
devtools::document()
devtools::test()
devtools::check()
```

If all checks and tests pass and the documentation is up to date, then push the commits to the GitHub repository.

```{bash}
git push
```

### Pull Requests

To merge the changes of your new branch into the `main` branch, please create a pull request with an overview of your changes in the description. Assign a reviewer (e.g., the maintainer) and keep an eye on potential comments and reviews to the pull request. The maintainer will merge the pull request to the `main` branch using `squash commits`.

Please note that the maintainer will not test your code but rather just shortly check if the code contradicts any previous changes. The responsibility of your code and its functionality within the package lies with you.

## Release Workflow

Creating new releases is pretty easy. The most important and time consuming part is to test whether everything works well.

Generally, new releases should be only created by the maintainer. If the maintainer is unavailable and a new release is indispensable, other contributors may create a release as well.

### Checks and Tests

At the moment, testing is done manually by comparing the results of the current version to results of the previous version using example NEPS data. In the future, automatic tests based on simulated data shall replace the manual tests. If bugs are found, they are fixed using the usual procedure using branches and pull requests.

Once all results are reproduced, please update the documentation and run all automatic tests and checks using the following commands:

```{r}
devtools::document()
devtools::test()
devtools::check()
```

### Create Release

Once all checks and tests pass, you can create a new release in five steps:

1.  **Update the DESCRIPTION and** **CITATION file** by changing the package version number and potentially adding new contributors as package authors or new features in the package description. The **version number** is given in the format vX.Y.Z. Change...
    1.  **X** for **breaking changes** (i.e., code is no longer backward compatible)
    2.  **Y** for **minor changes** (i.e., implemented new features, but still backward compatible)
    3.  **Z** for **minimal changes** (i.e., bug fixes, small improvements)

<!-- -->

2.  **Commit the changes** using a commit message that includes the new version name, e.g. "prepare release vX.Y.Z":

```{bash}
git commit -m "prepare release vX.Y.Z"
```

3.  **Create a** **tag** with the version name:

```{bash}
git tag vX.Y.Z
```

4.  **Push** both the commit and the new tag to the remote repository:

```{bash}
git push
git push --tags
```

5.  **Create a release** on GitHub: In the GitHub repository, go to "Releases". There, select your newly created tag "v.X.Y.Z". Select "create new release" and add changes since last release as release notes.

Congratulations, you've just created a new release! :)

### Create TAR-Ball

If required, create a TAR-ball from the release page on GitHub and send it to the FDZ or upload it on the Netzlaufwerk.

## Development Conventions

### Package Hygiene Rules

Not every document on GitHub needs to be included in releases. For example, development files (like this Rmd) can be specifically excluded by adding them in `.Rbuildignore`.

### Git Hygiene Rules

Only commit source code, documentation, and intentional data artifacts. Do NOT commit `.Rhistory` / `.RData` / `.Rproj.user` / generated files unless explicitly intended

### Documentation Workflow

Internal documentation is generated via `roxygen2`. NEVER manually edit `.Rd` files in `man/`.

External documentation is implemented via vignettes using simulated data. Major functions and features should be explained in the corresponding vignette.

### Dependency Workflow

When adding a new package dependency:

-   update `DESCRIPTION`

-   run `devtools::document()`

-   check `Imports` vs `Suggests`.

## Using AI for Package Development

*Here we could add rules / guidelines for incorporating AI in package development.*
