---
title: "Distractor Analyses"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Distractor Analyses}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

# General Information

In tasks where the respondent must choose between several answer options
(multiple choice), so-called distractors are used. These are incorrect
answers that are nevertheless constructed to resemble correct response
alternatives. A distractor analysis should be used in the context of
test evaluation to identify poor distractors. This is important because
poor distractors violate model assumptions and can lead to problems in
test interpretation. In the distractor analysis, point-biserial
correlations between the distractors and the total score of the
respondent are calculated.

The distractor analysis should only be conducted for all valid cases
(function argument `valid`). It is typically performed using the full
sample rather than separated by groups.

# Main Function

The function `dis_analysis()` computes correlations between correct or
incorrect item responses (distractors) and the total score. Distractors
are analysed for all raw multiple-choice items (function argument
`select_raw`). During data preparation, a corresponding variable was
already created in `vars`; in our example, it is called `distan`.

The output of the function consists of aggregated results reporting the
minimum and maximum correlations of correct responses and distractors
with the total score. In addition, a table is produced that details the
number of responses and the correlations between item responses and the
total score for each task. Both outputs are saved in Excel and RDS
format. If the file names need to be modified (e.g., because a test is
scaled simultaneously for several cohorts), use the function argument
`name_group` that adds a suffix to each file name (e.g., `"cohort_6"`).
A summary is printed in the console.

```{r}
NEPSroutines::dis_analysis(
  resp = resp,
  vars = vars,
  valid = "valid",
  select_raw = "distan",
  print = TRUE,
  save = FALSE,
  overwrite = TRUE,
  path_table = "tables",
  path_results = "results",
)
```

Information on the individual function arguments can be obtained via the
help function (`?dis_analysis`).

# Minor Functions

In addition to the main function, the following minor functions can be
used:

| Function | Input | Output |
|-------------------|----------------------------------|-------------------|
| `conduct_dis_analysis` | Data.frames `resp` and `vars` containing information on responses, items, and person characteristics | Results of the distractor analysis (R object, optionally RDS) |
| `dis_summary` | Output of the function `conduct_dis_analysis` (or the element `analysis` from the output of `dis_analysis`) | Tables with results of the distractor analysis (R object, optionally Excel) |
| `print_dis_summary` | Output of the function `dis_summary` (or the element `summary` from the output of `dis_analysis`) | Summary of the distractor analysis (printed in the console) |

Information on the individual function arguments can be obtained via the
help function (e.g., `?dis_summary`).
