---
title: "Create Scores"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Create Scores}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

# General Information

At the end of the scaling process, cross-sectional and longitudinal WLEs
are estimated and prepared for the SUF. In principle, WLEs are estimated
in the same way as in the Rasch or PCM analysis. Even if different test
booklets exist, all WLEs are calculated based on a jointly scaled model
(i.e., not separately by test booklet). If a rotation design is present,
a correction is applied in the cross-sectional estimation to obtain
unbiased ability estimates. For this purpose, the argument `facet` must
be specified accordingly.

For the estimation of cross-sectional WLEs, fixed item parameters can be
used. These item parameters correspond to the estimated item parameters
of the respective model and are available in the object created after
running the function `irt_analysis` (for example under
`irt_poly_all$model.pcm$mod$xsi$xsi`). This object element should be
provided in the argument `xsi_fixed`. Note that the fixed parameters
should be defined as a named numeric vector. This can be done, for
example, as follows:
`xsi_fixed = row.names(irt_poly_all$model.pcm$mod$xsi)`. If the argument
`xsi_fixed` is not specified, the function `create_scores()` will
automatically estimate the item parameters first and then use them for
the estimation of cross-sectional WLEs.

If more than one measurement occasion is available, linked item
parameters must additionally be used. However, linking is not yet
implemented in this version of the NEPSroutines package. In this case,
scores must be computed without the package.

# Provided Function

The function `create_scores()` returns a table with the newly computed
WLEs (variables with suffix `_sc1`) and the corresponding standard
errors (`_sc2`). If these WLEs are to be included in the SUF later
(which is usually the case), this table should be stored as an R object.
By default, the computed scores are saved in RDS format. In addition,
the item parameters used for WLE estimation are saved in XLSX format,
and the corresponding TAM model is saved in RDS format.

The package also allows the computation of sum scores and metacognitive
scores in addition to WLEs. Sum scores (variables with suffix `_sc3`)
require all original items used in the test. During data preparation
(see Section 4.3.3 Variables for Scores and the SUF), a variable should
therefore already have been created in `vars` that identifies all
dichotomous and polytomous items used in the test and included in the
SUF. These are scored items without collapsed categories. In the
example, this variable is called `suf`. To compute sum scores, the
argument `sum_score` must be set to `TRUE`, and the arguments
`sum_select` and `num_cat` must be specified. The computed sum scores
are stored as variables with suffix `_sc3`.

To compute metacognitive scores, the argument `metap` must be set to
`TRUE`, and the arguments `meta_variable`, `num_cat`, `meta_score_name`,
and `meta_select` must be specified. If either of the first two
arguments is missing, the function returns an error. If
`meta_score_name` or `meta_select` are missing, the function uses the
strings from `score_name` and `select` instead. The computed
metacognitive scores are stored as variables with suffix `_sc5` and
`_sc6`. Note that, unlike WLEs and sum scores, metacognitive scores are
computed separately for each test booklet. Therefore, it is recommended
to compute metacognitive scores separately from the other scores so that
`create_scores` can be specified separately for each booklet (e.g., by
selecting `suf_easy` or `suf_difficult` in `select`).

If the variable specified in `meta_variable` contains non-standard
values for metacognitive assessment (e.g., 5–10, 5/10), these values are
converted to `NA` during execution of `create_scores`. A warning message
is displayed in the console.

```{r}
scores <- NEPSroutines::create_scores(
  resp = resp,
  vars = vars,
  scoring = "scoring",
  score_name = "reg7",
  facet = NULL,
  select = "mixed",
  valid = "valid",
  wle = TRUE,
  sum_score = FALSE,
  sum_select = "suf",
  num_cat = "num_cat",
  metap = FALSE,
  return = TRUE
)
```

Information on the individual function arguments can be obtained via the
help function (`?create_scores`).
