---
title: "Create SUF"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Create SUF}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

# Main Function

The function `create_suf()` is used to create the SUF with the newly
computed WLEs. Note that all dichotomous and polytomous items used in
the test must be included in the SUF. These refer to the scored items.
Polytomous variables with collapsed categories should not be included in
the SUF. During data preparation, a logical variable should therefore
already have been created that identifies the relevant items (see
Section 4.3.3 Variables for Scores and the SUF). In the example, this
variable is called `suf`.

```{r}
NEPSroutines::create_suf(
  resp = resp,
  vars = vars,
  select = "suf",
  competence = "Reading",
  scores = scores,
  score_name = "reg7",
  path = "suf"
)
```

Information on the individual function arguments can be obtained via the
help function (`?create_suf`).

# Minor Functions

In addition to the main function `create_suf()`, the minor function
`set_labels()` can also be used. It allows changing the labels of items
in the SUF and returns a dataset that contains the SUF with the modified
labels.

Information on the individual function arguments can be obtained via the
help function (`?set_labels`).
