---
title: "Scaling NEPS data"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Scaling NEPS data}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

# Introduction

This scaling guide is primarily intended to introduce the general procedure of scaling of competence tests in the National Educational Panel Study (NEPS).

It is not intended as a comprehensive introduction to the methodological foundations of scaling or to the basics of R. The following sections provide only a brief overview of scaling in NEPS and working with R and mainly serve as pointers for further reading.

# Scaling of Competence Tests in NEPS

The scaling of competence tests in NEPS typically includes the following steps:

-   Data search and preparation\

-   Descriptive analysis\

-   Analysis of missing values (per person & per item)\

-   Item Response Theory (IRT) analyses\

-   Differential Item Functioning (DIF) analyses\

-   Distractor analyses\

-   Dimensionality analyses\

-   Linking\

-   Estimation of Weighted Maximum Likelihood Estimates (WLE)

-   Creation of the Scientific Use File (SUF)\

-   Documentation of results in the Technical Report (TR)

Individual steps may be omitted if the necessary prerequisites are not met (e.g., if no structure in the test justifies a dimensionality analysis).

This guide leads you step by step through these procedures starting in Chapter 4. Chapters 2 and 3 summarize key information on data preparation in R, required datasets, and the use of the `NEPSroutines` package. This chapter also provides background information on competence assessments and measurement models used in NEPS.

## Competence Assessments in NEPS

General information on competence assessments in NEPS is available at:

<https://www.neps-data.de/Portals/0/NEPS/Datenzentrum/Forschungsdaten/Kompetenzen/NEPS_OverviewCompetenceData_2025_en.pdf>

This document explains naming conventions and provides an overview of all competence assessments.

Further information on specific assessments can be found here:

<https://www.neps-data.de/Data-Center/Data-and-Documentation>

## Competence Items

Tasks in competence tests are called **items**. In the raw data, these are initially unscored and contain the response selected by the participant (e.g., “3” or "C" if the third option was chosen).

At the beginning of the scaling process, items are scored by converting them into dichotomous variables indicating whether the response is correct (1) or incorrect (0).

Some tasks consist of multiple sub-items (e.g., complex multiple-choice or matching tasks). These are called **polytomous items**. The score of a polytomous item is obtained by summing all sub-item scores. For example, an item with three sub-items can take the values 0, 1, 2, or 3.

During scaling, a distinction is made between dichotomous and polytomous items:

-   **Dichotomous items**: all simple scored items and all scored sub-items of polytomous items, as well as originally polytomous items reduced to two categories.
-   **Polytomous items**: all items with more than two categories.

## Item Response Theory Models

The scaling framework for NEPS is described in @pohl2012:

<https://www.neps-data.de/Portals/0/Working%20Papers/WP_XIV.pdf>

NEPS competence tests are designed to fit the Rasch model (@rasch1960) or the Partial Credit Model (PCM; @masters1982). Additionally, a 2PL model (@birnbaum1968) or a Generalized Partial Credit Model (GPCM; @muraki1992) is estimated to assess model fit.

The choice of model depends on the item format:

-   If only dichotomous items are present: Rasch model and 2PL model are used\
-   If at least one polytomous item is included: PCM and GPCM are used

## Linking

Competence assessments are often linked across waves or cohorts to ensure comparability between different measurements.

A detailed description of the linking procedure is provided in @fischer2016:

<https://www.neps-data.de/Portals/0/Survey%20Papers/SP_I.pdf>

*Note*: Linking is not yet implemented in this version of the `NEPSroutines` package.

# Basics in R

Basic knowledge of R is required to use this guide, including:

-   Loading packages\
-   Importing data\
-   Basic data manipulation (subsetting and merging datasets)

Key concepts include:

-   `NA` as missing value\
-   Data types: logical, numeric, integer, double, factor, character\
-   for-loops and if-statements\
-   Logical operators: `&`, `&&`, `|`, `||`, `!`, `==`, `!=`, `<=`, `>=`, `<`, `>`\
-   `%in%` operator\
-   Pipe operator `|>`\
-   Calling functions without loading packages: `package::function()`\
-   Indexing data frames:
    -   `df[rows, columns]`
    -   `df[[column]]`

If you are not familiar with R basics, many resources are available online (Stack Overflow is often helpful). R cheat sheets are also recommended:

<https://www.rstudio.com/resources/cheatsheets/>

Step-by-step execution of code helps with debugging.

# The `NEPSroutines` package

The data is scaled using the `NEPSroutines` package.

When installing and loading the package, all dependencies are automatically installed and loaded. Therefore, no additional packages need to be installed manually.

However, **NEPSroutines must be loaded at the beginning of each R session**.

If you need help with a function, you can use:

```{r}
help(function_name)
?function_name
```
