---
title: "Introduction to NEPSroutines"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Package Introduction}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

## Installing and Loading `NEPSroutines`

The NEPS data is scaled using the `NEPSroutines` package.

For this purpose, the latest stable version of `NEPSroutines` should be
installed (see README file for an how-to-guide).

Once installed, `NEPSroutines`must be loaded at the beginning of each R
session:

```{r}
library(NEPSroutines)
```

## Required Data Structure

Working with the `NEPSroutines` package requires a specific data
structure. This will be explained in the following section. How to
transform the raw data into the required data structure and which
functions of the `NEPSroutines` package may be helpful in this process
is described in Chapter 4 *Data Preparation*.

The package is mainly based on the two datasets `resp` and `vars`. The
**bold marked** variable names must be retained as specified. In all
other cases, variable names can be freely chosen.

### Groupings

Sometimes parts of the scaling procedure are conducted separately for
different groups, e.g. different test versions, settings, measurement
occasions, or cohorts. The terms *group* and *grouping* refer to such
cases. However, the functions of the package can only handle one
grouping at a time. If multiple groupings are present (e.g. different
test booklets *and* different cohorts), there are two possible
approaches:

-   On the one hand, analyses can be conducted separately. Since the
    functions of the package can handle at least one grouping, it is
    sufficient to run the analyses separately for the groups of the
    second grouping (e.g. once for cohort A and once for cohort B). The
    first grouping (in our case test booklet version) can then be
    handled normally within the functions. In this case, remember to
    assign a group name using the function argument `name_group`, so
    that results are saved under different names and can be clearly
    assigned to the respective groups (cohort A, cohort B).

-   On the other hand, a grouping variable can be created that contains
    *all* possible combinations of groupings. This can then be used as a
    standard grouping variable in the functions. For two groupings with
    two levels each (e.g. cohorts A and B, test booklets A and B), a new
    grouping variable with four categories would need to be created:

    -   Group 1 for cohort A & test booklet A

    -   Group 2 for cohort A & test booklet B

    -   Group 3 for cohort B & test booklet A

    -   Group 4 for cohort B & test booklet B

### Dataset `resp`

This dataset (`data.frame`) contains all competence items — both scored
and unscored — as well as all information about the test participants,
e.g. sociodemographic variables. Information about each participant is
stored in a single row. An example of this dataset can be seen below for
study B129. The following variables are particularly required:

+------------------------+--------------------------------------------+
| Variable               | Explanation                                |
+========================+============================================+
| **`ID_t`**             | A variable that contains the IDs of the    |
|                        | persons.                                   |
+------------------------+--------------------------------------------+
| All sociodemographic   | -   The variables must be numeric. All     |
| and methodological     |     variables used in the DIF analyses     |
| variables available    |     must be dichotomous in {0, 1}.         |
| per test person        |     Non-inherently dichotomous variables   |
|                        |     can be dichotomized, e.g. categorizing |
|                        |     number of books at home into \> 100    |
|                        |     books and \< 100 books. Variables used |
|                        |     only for descriptive analyses, e.g.    |
|                        |     age in schoolchildren, may also be     |
|                        |     continuous.                            |
|                        |                                            |
|                        | -   Missing values are defined as NA       |
|                        |                                            |
|                        | -   For an overview of all variables       |
|                        |     required for scaling, see vignette     |
|                        |     `preparations`.                        |
+------------------------+--------------------------------------------+
| All unscored, scored,  | -   All unscored items may be numeric,     |
| and aggregated         |     character, or factor variables.        |
| competence items       |                                            |
|                        | -   All scored items must be integers.     |
|                        |     Either dichotomous in {0, 1} or, for   |
|                        |     polytomous items with k categories, in |
|                        |     {0, 1, ..., k-1}.                      |
|                        |                                            |
|                        | -   Missing values are coded using         |
|                        |     negative integers that distinguish     |
|                        |     between cases, e.g. -91 = test         |
|                        |     aborted, -55 = not administered. These |
|                        |     values are referred to as              |
|                        |     *user-defined missing values* and      |
|                        |     should already be present in the raw   |
|                        |     data.                                  |
+------------------------+--------------------------------------------+
| Additional variables   | -   **Validity variable** e.g. `valid`:    |
| that identify specific |     Identifies those persons who have      |
| persons in the dataset |     reached a minimum number of valid      |
|                        |     responses to be included in the        |
|                        |     analyses. In our scaling procedures,   |
|                        |     this is typically *three* valid        |
|                        |     responses.                             |
|                        |                                            |
|                        |     -   The variable must be logical.      |
|                        |                                            |
|                        |     -   TRUE for all persons with the      |
|                        |         minimum number of valid responses  |
|                        |                                            |
|                        | -   **Group and grouping variables**, if   |
|                        |     one or more groupings are present      |
|                        |                                            |
|                        |     -   For each grouping, a numeric or    |
|                        |         factor variable must be created    |
|                        |         that assigns each person to a      |
|                        |         group e.g. `difficulty`, with      |
|                        |         `0=easy` & `1=difficult`           |
|                        |                                            |
|                        |     -   In addition, a logical variable    |
|                        |         must be created per group e.g.     |
|                        |         `easy` *and* `difficult` that      |
|                        |         identifies all persons belonging   |
|                        |         to that group                      |
|                        |                                            |
|                        |     -   If items were administered to both |
|                        |         groups, an IRT analysis is usually |
|                        |         also performed for all common      |
|                        |         items. For this purpose, a         |
|                        |         variable must be defined in `resp` |
|                        |         e.g. `common` that is TRUE for all |
|                        |         persons who received the common    |
|                        |         items — i.e. for all persons!      |
|                        |                                            |
|                        | -   In individual cases, additional        |
|                        |     variables may be required              |
+------------------------+--------------------------------------------+

Example for `resp` (from study B129, only the first variables are
shown):

+----------------+-----------------------------------------------------+
| Variable       | Explanation                                         |
+================+=====================================================+
| **`ID_t`**     | Contains the IDs of the persons                     |
+----------------+-----------------------------------------------------+
| `sex`,         | Dichotomous (or dichotomized) sociodemographic      |
| `migration`    | variables for descriptive and DIF analyses          |
| and `books`    |                                                     |
+----------------+-----------------------------------------------------+
| `difficulty`   | Grouping variable assigning persons to the          |
|                | different test booklets                             |
+----------------+-----------------------------------------------------+
| `easy` and     | Group variables identifying persons who received    |
| `difficult`    | the easy or difficult test form                     |
+----------------+-----------------------------------------------------+
| `valid`        | Validity variable identifying all persons who have  |
|                | provided at least three valid responses             |
+----------------+-----------------------------------------------------+
| `r             | Unscored simple item with user-defined missing      |
| eg70110_sc2g7` | values                                              |
+----------------+-----------------------------------------------------+
| `re            | Unscored sub-items of a polytomous item with        |
| g70131_sc2g7`, | user-defined missing values                         |
| `re            |                                                     |
| g70132_sc2g7`, |                                                     |
| `r             |                                                     |
| eg70133_sc2g7` |                                                     |
+----------------+-----------------------------------------------------+
| `reg           | The dichotomously scored item belonging to          |
| 70110_sc2g7_c` | `reg70110_sc2g7` (recognizable by the suffix `_c`)  |
|                | with user-defined missing values                    |
+----------------+-----------------------------------------------------+
| `reg           | The polytomously scored item belonging to the       |
| 7013s_sc2g7_c` | sub-items (recognizable by the `s` at the end of    |
|                | the item stem and the `_c` suffix) with             |
|                | user-defined missing values                         |
+----------------+-----------------------------------------------------+

### Dataset `vars`

This dataset (`data.frame`) contains all information about the
competence items, e.g. item positions, assignment to a test booklet, and
item type. Each version of a competence item (e.g. scored and unscored)
is stored in a separate row (for an overview of the different item
types, see Section *Competence items* in vignette `scaling_NEPS_data`).
An example of the `vars` dataset can be seen below for study B129. How
the variables are constructed is described in Chapter 4 *Data
Preparation*. The following variables are particularly required:

+----------------------------------+----------------------------------+
| Variable                         | Explanation                      |
+==================================+==================================+
| **`item`**                       | A variable containing the item   |
|                                  | name                             |
+----------------------------------+----------------------------------+
| `correct_response`               | A variable containing the        |
|                                  | correct answer of the respective |
|                                  | item e.g. 3 if the third         |
|                                  | response option is correct. Can  |
|                                  | be a character or numeric        |
|                                  | vector.                          |
+----------------------------------+----------------------------------+
| `type`                           | Variable defining the item type  |
|                                  | MC, CMC, etc.                    |
+----------------------------------+----------------------------------+
| Position variables               | Indicate the position of the     |
|                                  | item in the test booklet         |
|                                  |                                  |
|                                  | -   If there are multiple        |
|                                  |     groups, one position         |
|                                  |     variable per group, even if  |
|                                  |     the position is identical    |
|                                  |     across groups                |
|                                  |                                  |
|                                  | -   Otherwise only one position  |
|                                  |     variable                     |
+----------------------------------+----------------------------------+
| Logical variables identifying    | -   `raw`: TRUE for all          |
| specific items                   |     *unscored* items raw data    |
|                                  |                                  |
|                                  | -   `distan`: TRUE for all       |
|                                  |     *unscored* *multiple-choice* |
|                                  |     items required for           |
|                                  |     distractor analysis          |
|                                  |                                  |
|                                  | -   `dich`: TRUE for all         |
|                                  |     *dichotomously scored* items |
|                                  |     used e.g. for IRT and DIF    |
|                                  |     analyses. This also includes |
|                                  |     sub-items of polytomous      |
|                                  |     items!                       |
|                                  |                                  |
|                                  | -   If the item set also         |
|                                  |     includes polytomous items:   |
|                                  |                                  |
|                                  |     -   `poly`: TRUE for all     |
|                                  |         *polytom scored* items   |
|                                  |         used for data            |
|                                  |         preparation              |
|                                  |                                  |
|                                  |     -   `final`: TRUE for all    |
|                                  |         items to be used in      |
|                                  |         scaling used e.g. for    |
|                                  |         IRT and DIF analyses.    |
|                                  |         This initially includes  |
|                                  |         all *dichotomously       |
|                                  |         scored* items            |
|                                  |         *excluding* sub-items of |
|                                  |         polytomous items and all |
|                                  |         *polytomously scored*    |
|                                  |         items if an item was     |
|                                  |         collapsed, then the      |
|                                  |         version with collapsed   |
|                                  |         response categories.     |
|                                  |                                  |
|                                  | -   If the item set changes      |
|                                  |     during scaling e.g. because  |
|                                  |     items are excluded, new      |
|                                  |     variables must be created    |
|                                  |     e.g. `dich_new` or           |
|                                  |     `final_new` that replace the |
|                                  |     variables above for the new  |
|                                  |     item set required for all    |
|                                  |     analyses.                    |
|                                  |                                  |
|                                  | -   `suf`: TRUE for all *scored* |
|                                  |     items without collapsed      |
|                                  |     response categories that are |
|                                  |     actually used in the test    |
|                                  |     used for computation of sum  |
|                                  |     scores, metacognition        |
|                                  |     scores, and creation of the  |
|                                  |     SUF.                         |
+----------------------------------+----------------------------------+
| Depending on scaling additional  | -   **Grouping variables**, if   |
| variables                        |     not all items are            |
|                                  |     administered in every group  |
|                                  |     e.g. different test booklet  |
|                                  |     versions usually contain     |
|                                  |     different item sets          |
|                                  |                                  |
|                                  |     -   Group variables are      |
|                                  |         always logical variables |
|                                  |                                  |
|                                  |     -   One variable per group   |
|                                  |         e.g. `easy` and          |
|                                  |         `difficult` for easy and |
|                                  |         difficult test forms     |
|                                  |                                  |
|                                  |     -   If items are             |
|                                  |         administered to all      |
|                                  |         groups, an additional    |
|                                  |         variable e.g. `common`   |
|                                  |         must be created          |
|                                  |         identifying these items  |
|                                  |                                  |
|                                  |     -   For each grouping        |
|                                  |         variable e.g. `easy`,    |
|                                  |         `difficult` & `common`   |
|                                  |         and analysis variable    |
|                                  |         e.g. `dich`, `final` &   |
|                                  |         `suf`, a new             |
|                                  |         group-specific analysis  |
|                                  |         variable must be created |
|                                  |         e.g. `dich_easy`         |
|                                  |         identifying all          |
|                                  |         dichotomous items of the |
|                                  |         easy test form.          |
|                                  |                                  |
|                                  | -   **Scoring variables**, if    |
|                                  |     polytomous items are         |
|                                  |     included e.g. `scoring`.     |
|                                  |     These are needed for PCM and |
|                                  |     GPCM estimation. The scoring |
|                                  |     defines how strongly an item |
|                                  |     contributes to the analysis. |
|                                  |     By default, this is 0.5 for  |
|                                  |     polytomous items and 1 for   |
|                                  |     dichotomous items, but       |
|                                  |     deviations are possible in   |
|                                  |     individual cases.            |
|                                  |                                  |
|                                  | -   **Dimensionality             |
|                                  |     variables**, if the test     |
|                                  |     structure may violate        |
|                                  |     unidimensionality e.g.       |
|                                  |     reading tests with multiple  |
|                                  |     task groups.                 |
|                                  |                                  |
|                                  | -   **Linking variables**, if    |
|                                  |     linking is performed after   |
|                                  |     scaling. The required        |
|                                  |     variables depend on the type |
|                                  |     of linking and data. See     |
|                                  |     Survey Paper No. 1 Fischer   |
|                                  |     et al., 2016; link above.    |
|                                  |                                  |
|                                  | -   In individual cases,         |
|                                  |     additional variables may be  |
|                                  |     required                     |
+----------------------------------+----------------------------------+

An example of `vars` (from study B129, only the first variables are
shown):

+----------------+-----------------------------------------------------+
| Argument       | Explanation                                         |
+================+=====================================================+
| `item`         | Contains the item names                             |
+----------------+-----------------------------------------------------+
| `type` and     | Variables defining item type and correct response   |
| `cor           |                                                     |
| rect_response` |                                                     |
+----------------+-----------------------------------------------------+
| `raw`, `dich`  | Logical variables identifying unscored,             |
| and `poly`     | dichotomously scored, and polytomously scored items |
+----------------+-----------------------------------------------------+
| `distan`       | Logical variable identifying all items required for |
|                | distractor analysis (unscored multiple-choice       |
|                | items)                                              |
+----------------+-----------------------------------------------------+
| `final`        | Logical variable identifying all items included in  |
|                | IRT analyses. Includes all inherently dichotomous   |
|                | items and all polytomous items. If items are        |
|                | excluded or collapsed during scaling, this variable |
|                | may be updated or replaced (e.g. `final_new`)       |
+----------------+-----------------------------------------------------+
| `easy`,        | Logical group variables identifying items belonging |
| `difficult`    | to the easy, difficult, or both test versions       |
| and `common`   |                                                     |
+----------------+-----------------------------------------------------+
| `suf`          | Logical variable identifying items used for score   |
|                | computation and included in the SUF                 |
+----------------+-----------------------------------------------------+
| `text_type`    | Variables for dimensionality analyses               |
| and `kog_type` |                                                     |
+----------------+-----------------------------------------------------+
| `scoring`      | Scoring variable required for PCM and GPCM          |
+----------------+-----------------------------------------------------+
| `              | Position variables specifying item position         |
| position_easy` | separately for both test booklets                   |
| and            |                                                     |
| `              |                                                     |
| position_diff` |                                                     |
+----------------+-----------------------------------------------------+
| `dich_easy`,   | Logical variables identifying dichotomously scored  |
| `di            | items from the easy, difficult, or both test        |
| ch_difficult`, | versions                                            |
| `dich_common`  |                                                     |
+----------------+-----------------------------------------------------+
| `final_easy`,  | Logical variables identifying polytomously scored   |
| `fin           | and inherently dichotomous items from the different |
| al_difficult`, | test versions                                       |
| `final_common` |                                                     |
+----------------+-----------------------------------------------------+
| `suf_easy` and | Logical variables identifying items used for score  |
| `              | computation and SUF creation for each test version  |
| suf_difficult` |                                                     |
+----------------+-----------------------------------------------------+

### Example Data

You can find the example data in the folder `data/` within the
`NEPSroutines` package. The package includes the following example data:

-   `ex1.Rda`: SHORT DESCRIPTION

-   `ex2.Rda`: SHORT DESCRIPTION

-   `ex3.Rda`: SHORT DESCRIPTION

-   `ex4.Rda`: SHORT DESCRIPTION

## Package Structure

The package is strongly oriented toward the scaling of NEPS competence
tests and includes functions for the following sections of the scaling
process:

-   Data preparation

-   Descriptive analyses

-   Analysis of missing values (per person & per item)

-   IRT analyses

-   DIF analyses

-   Distractor analysis

-   Dimensionality analysis

-   Score creation

-   SUF creation

-   Technical report

With the exception of data preparation and descriptive analyses, there
is a single **main function** for each scaling section that
automatically performs all necessary calculations and returns results as
plots, tables, and messages. However, there are also **minor functions**
that allow individual steps of each section to be performed separately,
enabling users to refine the original analyses or adapt them to specific
needs. In the corresponding vignettes within this guide, the main
functions are presented in detail, while the minor functions are only
briefly described.

In addition to the section functions, the package contains general
functions (see Section \@ref(Helper Functions)) that may be useful for
scaling outside the predefined framework.

### Function Output

The output of the main functions usually consists of optionally
generated summary results as an Excel table (function argument
`save=TRUE`), the original results in RDS format (function argument
`save=TRUE`), and additional information printed to the console
(function argument `print=TRUE`). Depending on the function, plots may
also be generated (function argument `plots=TRUE`). The tables are
typically designed so that they can be used directly for reporting. The
original results are usually stored as a list containing the unmodified
output of the underlying functions (e.g. TAM functions). These results
can also be printed directly in R (function argument `return=TRUE`). If
they are stored in an R object (by assigning them a name), they can be
further processed directly. For example:

```{r}
irt_results <- irt_analysis()
```

For minor functions that perform analyses, a list of results is always
returned. This output, or parts of it, is usually required for
subsequent functions (e.g. for generating plots or result tables). It is
therefore recommended to store the output in an R object (see above).
When using downstream functions, pay close attention to the instructions
in this guide and in the help files (see vignette `general_information`)
regarding which output or which part of the output is actually required!
For minor functions that generate plots or tables from results, users
can choose whether these files should be saved (function argument
`save=TRUE`).

### Common Function Arguments

The functions in the package are partially structured in a very similar
way, so that many function arguments are repeated. The most common
arguments are presented in this section, but are not explained in
further detail in the remainder of the guide.

**Input** arguments:

+---------+---------+-------------------------------------+---------+
| A       | Type    | Description                         | Default |
| rgument |         |                                     |         |
+=========+=========+=====================================+=========+
| `resp`  | data    | These function arguments require    |         |
| and     | frame   | the data frames `resp` and `vars`   |         |
| `vars`  |         | introduced in the previous section. |         |
|         |         | They can be passed as they are and  |         |
|         |         | do not need to be modified further. |         |
+---------+---------+-------------------------------------+---------+
| `       | string  | The analyses are almost always      |         |
| select` |         | based on only a subset of the       |         |
|         |         | available items or only a specific  |         |
|         |         | version of the items. This function |         |
|         |         | argument requires the name of the   |         |
|         |         | logical variable in `vars` that     |         |
|         |         | identifies the variables required   |         |
|         |         | for this analysis e.g. `dich` for   |         |
|         |         | only dichotomous items or `scaling` |         |
|         |         | for dichotomous *and* polytomous    |         |
|         |         | items.                              |         |
+---------+---------+-------------------------------------+---------+
| `valid` | string  | Optional in most functions. This    | all     |
|         |         | function argument requires the name | cases   |
|         |         | of the logical variable in `resp`   | are     |
|         |         | that identifies all valid cases see | used    |
|         |         | section *Valid Cases* in vignette   |         |
|         |         | `prepare_data`.                     |         |
+---------+---------+-------------------------------------+---------+
| `mvs`   | named \ | Optional in most functions          | -999 to |
|         | ch      | exception: missing value analysis.  | -1      |
|         | aracter | Requires a named character vector   |         |
|         | vector  | containing all user-defined missing |         |
|         |         | values see section *User-Defined    |         |
|         |         | Missing Values* in vignette         |         |
|         |         | `prepare_data`. Warning: If this    |         |
|         |         | vector is incomplete, severe        |         |
|         |         | problems and errors in scaling may  |         |
|         |         | occur!                              |         |
+---------+---------+-------------------------------------+---------+
| `gr     | ch      | Optional in some functions.         | NULL    |
| ouping` | aracter | Sometimes parts of the scaling must |         |
|         | vector  | be conducted separately for         |         |
|         |         | different groups e.g. different     |         |
|         |         | test booklet versions. In this      |         |
|         |         | case, this function argument        |         |
|         |         | requires a character vector with    |         |
|         |         | the names of the logical variables  |         |
|         |         | in `resp` and `vars` that identify  |         |
|         |         | all persons or items belonging to a |         |
|         |         | group. One name is specified per    |         |
|         |         | group. Variable names must match    |         |
|         |         | between `resp` and `vars` e.g. the  |         |
|         |         | variable `easy` in `vars`           |         |
|         |         | identifies all items administered   |         |
|         |         | in the easy test version, and the   |         |
|         |         | variable `easy` in `resp`           |         |
|         |         | identifies all persons who          |         |
|         |         | completed the easy test version.    |         |
+---------+---------+-------------------------------------+---------+

**Process** arguments:

+----------+----------+------------------------------------+----------+
| Argument | Type     | Description                        | Default  |
+==========+==========+====================================+==========+
| `digits` | integer  | Number of decimal places to which  | usually  |
|          |          | the results should be rounded.     | `3`      |
+----------+----------+------------------------------------+----------+
| `warn`   | logical  | Whether warnings should be printed | usually  |
|          |          | to the console.                    | `TRUE`   |
+----------+----------+------------------------------------+----------+
| `        | logical  | Whether the processing steps       | usually  |
| verbose` |          | should be printed to the console.  | `TRUE`   |
+----------+----------+------------------------------------+----------+

**Output** arguments:

+----------+----------+-----------------------------------+----------+
| Argument | Type     | Description                       | Default  |
+==========+==========+===================================+==========+
| `plots`  | logical  | In main functions, users can      | usually  |
|          |          | choose whether plots of the       | `FALSE`  |
|          |          | analyses (e.g. ICC plots and      |          |
|          |          | Wright maps in IRT analyses)      |          |
|          |          | should be generated.              |          |
+----------+----------+-----------------------------------+----------+
| `print`  | logical  | In main functions, users can      | usually  |
|          |          | choose whether (additional)       | `TRUE`   |
|          |          | results should be printed to the  |          |
|          |          | console or included in the HTML   |          |
|          |          | document.                         |          |
+----------+----------+-----------------------------------+----------+
| `save`   | logical  | In almost all functions, users    | usually  |
|          |          | can choose whether results should | `TRUE`   |
|          |          | be saved (as `Excel` and/or       |          |
|          |          | `RDS`).                           |          |
+----------+----------+-----------------------------------+----------+
| `return` | logical  | In main functions, users can      | usually  |
|          |          | choose whether results should be  | `FALSE`  |
|          |          | returned in R (as `Rdata`).       |          |
+----------+----------+-----------------------------------+----------+
| `path`   | string   | Path where results should be      | `"Re     |
|          |          | stored. If the specified folder   | sults"`, |
|          |          | does not exist, it will be        | `"       |
|          |          | created automatically. In main    | Plots",` |
|          |          | functions, this is split into     | `"       |
|          |          | `path_results`, `path_plots`, and | Tables"` |
|          |          | `path_table`.                     |          |
+----------+----------+-----------------------------------+----------+
| `ov      | logical  | Whether Excel tables should be    | `FALSE`  |
| erwrite` |          | overwritten if they already       |          |
|          |          | exist.                            |          |
+----------+----------+-----------------------------------+----------+
| `nam     | string   | Name of the *group* to which the  | `NULL`   |
| e_group` |          | analyses refer (e.g. "easy", see  |          |
|          |          | 3.1.1 *Groupings*), used to label |          |
|          |          | results, tables, and figures      |          |
|          |          | accordingly by adding a suffix to |          |
|          |          | the file name. Do not confuse     |          |
|          |          | this with `name_grouping` (= name |          |
|          |          | of the *grouping*, e.g. "test     |          |
|          |          | version") in `mv_person` and      |          |
|          |          | `mv_item`!                        |          |
+----------+----------+-----------------------------------+----------+

In some functions, additional specific arguments are included. These are
described in this guide and can also be accessed at any time via the R
documentation (using the helper functions, see vignette
`general_information`).

### Helper Functions

If parts of the scaling process are carried out without the
corresponding package functions, some of the following functions may be
helpful.

+--------------+-------------------------------------------------------+
| Function     | Usage                                                 |
+==============+=======================================================+
| `convert_mv` | Converts user-defined missing values into NAs. Input  |
|              | arguments are `resp`, `items`, and `mvs`. The output  |
|              | is `resp` with converted missing values.              |
+--------------+-------------------------------------------------------+
| `p           | Prepares `resp` for subsequent analyses. Input        |
| repare_resp` | arguments are `resp`, `vars`, `items`, `valid`,       |
|              | `mvs`, the logical `use_only_valid` (whether only     |
|              | valid cases should be used), and the logical          |
|              | `convert` (whether user-defined missing values should |
|              | be converted to NAs). The output is `resp` containing |
|              | only the items defined in `items` as variables,       |
|              | optionally restricted to valid cases and with missing |
|              | values optionally converted to NAs.                   |
+--------------+-------------------------------------------------------+
| `c           | Checks whether the folder specified in the path       |
| heck_folder` | exists and creates it if it does not.                 |
+--------------+-------------------------------------------------------+
| `meht`       | Performs the Minimum Effect Hypothesis Test. Input    |
|              | arguments are various statistical quantities.         |
+--------------+-------------------------------------------------------+

## Debugging

Step-by-step execution of code helps with debugging.

Since every scaling procedure is slightly different, it is possible that
errors occur when using the NEPSroutines package. However, in many
cases, the cause of error messages is simply issues in the data
themselves. If a function produces an error message, first check whether
your data are correct: Are all item properties in the `vars` dataset
correctly defined? Does every item in `vars` also appear in `resp` and
vice versa? Do the variable classes match the required specifications?
Have the variables been named correctly? The required data structure is
described in detail in the previous section *Required Data Structure*
and can be partially checked using dedicated functions (see vignette
`prepare_data`).

If the data are correct and the error still occurs, you can contact
*skalierung\@lifbi.de* with the error message, your script, and the
data.
