---
title: "Import Data"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Import Data}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

# Required Data and Files

Scaling requires multiple datasets that usually need to be assembled manually. This section provides an overview of the most commonly required data and their typical locations. Exceptions may apply depending on the specific study.

Most relevant files can be found in:

`//wipo.lifbi.de/daten/Projektgruppen_(08)/Kompetenzen_BA_Hiwi_(p000012)/Methoden/Skalierung/HE`

Within each sub-study folder, SPSS files and codebooks are typically located in the `rawdata` folder (sometimes within `preloads`).

If a required file is missing, it should be requested.

## Competence Data

Competence data are contained in SPSS files with `xTargetCompetencies` in the file name.

Required variables include the ID variable (`ID_t`) and all competence items. Item names can be found in the respective study documentation or codebook. Only data from the relevant wave should be retained.

## Information on Competence Items

For scaling, additional item-level information is required, including:

-   Item position (may vary across test booklets)

-   Item type (e.g., multiple choice, constructed response)

-   Correct response

-   Test booklet assignment

-   Item cluster or group

-   Additional variables depending on the study (e.g., content domain)

This information must typically be extracted from test booklets, study design documentation, or survey materials and ideally compiled into an Excel file.

Relevant documents can often be found here:

`//wipo.lifbi.de/daten/Projekte_(07)/NEPS-Kompetenzen_(14)/Netzwerk_(05)`

## Sociodemographic Data

In addition to competence items, sociodemographic variables are required for descriptive analyses and DIF analyses. Depending on the study type, these may include gender, migration background, cultural capital (e.g., number of books at home as part of socioeconomic status), school type (for students in secondary education), educational attainment (for adults), and age (for adults; in school samples this is typically homogeneous due to grade-level structure).

These variables can be found in SPSS files such as `CohortProfile`, `pParent` (children), or `pTarget` (adults).

Common variable names (may vary by study):

-   **Gender**: `tx80501` in `CohortProfile`

-   **Age**: must be computed (see vignette `data_preparation`) using `tx8050y` (year of birth), `tx8050m` (month of birth), and the survey year/month in `CohortProfile`

-   **Migration background**: e.g., `p400500_g1` in `pParent` (children)

-   **Cultural capital**: e.g., `p34005a` in `pParent` (children)

All other variables should be verified using the respective codebook.

## Test Booklet Design Information

In addition to competence and sociodemographic data, information on survey design and test booklet structure is required.

Many studies use multiple test booklets (e.g., easy vs. difficult forms) and/or rotational designs in which different groups receive different test orders (e.g., Group 1: Reading → Mathematics; Group 2: Mathematics → Reading).

This information is typically stored in the SPSS file `xTargetCompetencies` in a variable whose name starts with `tx` and whose label contains *"survey/test instrument"*.

Since values are encoded numerically, value labels must be used to interpret them. In SPSS, these can be viewed in variable view.

In R, labels can be retrieved (after importing the data with `haven`) using:

```{r}
attributes(dat$name_variable)$labels
```

# Import Data
