---
title: "Missing Values Analyses"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Missing Values Analyses}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

# General Information

For scaling a test, it is important to analyse the different types of
missing values, i.e. to examine the reasons for missing responses and
how often they occur. For NEPS tests, this is done on the one hand per
person (how many items were not answered on average per person and for
what reason) and on the other hand per item (how many persons answered
or did not answer an item and for what reason). To conduct these
analyses, missing values of the competency items must be coded as
user-defined missing values. Which values are typically used in NEPS and
how to create the function arguments `mvs` and `labels_mvs` is described
in Section 4.1.4.

The analyses should only be conducted for all valid cases (function
argument `valid`). Only those items (function argument `select`) that
are also used for the final IRT scaling should be considered (in most
cases `dich` or `mixed`, depending on the composition of the item set).
The results of the analyses are automatically saved in RDS format. The
summary of the results is saved as an Excel file and printed to the
console. To generate and save plots, the function argument `plots` must
be set to `TRUE`.

# Analysis of Missing Values per Person

## General Function

The function `mv_person()` is used to analyse missing values per person.
This analysis includes information on all user-defined missing values
specified in the argument `mvs`. In addition, statistics are also
computed for all missing values jointly defined in `mvs`. Missing values
not included in `mvs` are not included in this sum. It is therefore
important to include all existing user-defined missing values in `mvs`
if the aggregate value (“ALL”) is to be meaningfully interpreted. An
exception are design-related missing responses, which are automatically
excluded from the dataset prior to the analysis. For this purpose, the
corresponding user-defined missing value must be specified in the
argument `missing_by_design` (default is `-54`). It is very important to
specify the correct value here, otherwise incorrect responses will be
filtered out and the number of persons to whom each item was
administered will also be incorrect.

The analyses can also be conducted separately for different groups
(e.g., test booklets). These must be defined in the argument `grouping`.
Missing values are then calculated per group only for the items that
were also administered to that group. The name of the grouping (e.g.,
“test version”) can be specified using the argument `name_grouping` for
labelling the plots. If results are required not only by group but also
for the total sample (both in tables and plots), the argument `show_all`
must be set to `TRUE`.

```{r}
NEPSroutines::mv_person(
  resp = resp,
  vars = vars,
  select = "mixed",
  valid = "valid",
  grouping = c("easy", "difficult"),
  mvs = mvs,
  labels_mvs = labels_mvs,
  missing_by_design = -54,
  plots = TRUE,
  print = TRUE,
  save = TRUE,
  return = FALSE,
  path_results = ("Results"),
  path_table = ("Tables"),
  path_plots = ("Plots/Missing_Responses/by_person"),
  show_all = FALSE,
  overwrite = TRUE,
  name_grouping = "test version",
  digits = 3
)
```

Information on how to use the individual function arguments can be found
via the help function (e.g. `?mvp_analysis`).

## Subordinate Functions

In addition to the main function, the following subordinate functions
can be used:

| Function | Input | Output |
|------------------|------------------------------|-----------------------|
| `mvp_analysis` | Data.frames `resp` and `vars` containing information on responses, items, person characteristics, and optionally grouping | Results of the MVP analyses (R object, optionally RDS) |
| `mvp_plots` | Output of the function `mvp_analysis` or the element `mv_p` from the output of `mv_person` | Plots for each user-defined missing value type (PNG) |
| `mvp_table` | Output of the function `mvp_analysis` or the element `mv_p` from the output of `mv_person` | Table with results of the MVP analyses for the Technical Report (R object, optionally Excel) |
| `print _mvp_results` | Output of the function `mvp_analysis` or the element `mv_p` from the output of `mv_person` | Summary of the MVP analysis results (printed in the console) |

Information on how to use the individual function arguments can be found
via the help function (e.g. `?mvp_analysis`).

# Analysis of Missing Values per Item

## General function

Similar to the function `mv_person()`, missing values can also be
analysed using the function `mv_item()`. The difference compared to the
function described above is that the proportions of specific missing
values are now displayed for each item rather than per person.
Information is again provided for all user-defined missing values
specified in the argument `mvs`. As before, statistics are also computed
for all missing values jointly defined in `mvs`. Missing values not
included in `mvs` are not considered in this sum. It is therefore
important to include all existing user-defined missing values in `mvs`
if the aggregated value (“ALL”) is to be meaningfully interpreted. An
exception are design-related missing responses, which are automatically
excluded from the dataset prior to the analysis. For this purpose, the
corresponding user-defined missing value must be specified in the
argument `missing_by_design` (default is `-54`). It is very important to
specify the correct value here; otherwise, incorrect responses will be
filtered out and the number of persons to whom each item was
administered will also be incorrect.

The analyses can also be conducted separately for different groups
(e.g., test booklets). These must be defined in the argument `grouping`.
Missing values are then calculated per group only for the items that
were administered to that group. The name of the grouping (e.g., “test
version”) can be specified using the argument `name_grouping` for
labelling the plots. Missing values per item are displayed depending on
item position and, if applicable, grouping.

By setting the argument `save` to `TRUE`, results can be saved in `.rds`
and `.xlsx` files. The results from the Excel file can, for example, be
used in the Technical Report. If the argument `suf_item_names` is set to
`TRUE`, the names of polytomous items with collapsed categories are
displayed without the suffix `"_collapsed"`. By default
(`suf_item_names = FALSE`), item names remain unchanged. Note that in
`.rds` files, item names always remain unchanged.

```{r}
NEPSroutines::mv_item(
  resp = resp,
  vars = vars,
  select = "mixed",
  valid = "valid",
  grouping = c("easy", "difficult"),
  mvs = mvs,
  labels_mvs = labels_mvs,
  missing_by_design = -54,
  position = c(easy = "position_easy_mixed",
               difficult = "position_difficult_mixed"),
  plots = TRUE,
  print = TRUE,
  save = TRUE,
  return = FALSE,
  path_results = ("Results"),
  path_table = ("Tables"),
  path_plots = ("Plots/Missing_Responses/by_item"),
  suf_item_names = TRUE,
  show_all = FALSE,
  overwrite = TRUE,
  name_grouping = "test version",
  digits = 3
)
```

Information on how to use the individual function arguments can be found
via the help function (e.g. `?mvi_analysis`).

## Subordinate Functions

In addition to the main function, the following subordinate functions
can be used:

| Function | Input | Output |
|------------------------|------------------------|------------------------|
| `mvi_analysis` | Data.frames `resp` and `vars` containing information on responses, items, person characteristics, and optionally grouping | Results of the MVI analyses (R object, optionally RDS) |
| `mvi_plots` | Output of the function `mvi_analysis` (or element `mv_i` from the output of `mv_item`) | Plots for each user-defined missing value type (PNG) |
| `mvi_table` | Output of the function `mvi_analysis` (or element `mv_i` from the output of `mv_item`) | Table with results of the MVI analyses for the Technical Report (R object, optionally Excel) |
| `print_mvi_results` | Output of the function `mvi_analysis` (or element `mv_i` from the output of `mv_item`) | Summary of the MVI analysis results (printed in the console) |

Information on how to use the individual function arguments can be found
via the help function (e.g. `?mvi_analysis`).

# [Include information on multistage tests]
