---
title: "IRT Analyses"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{IRT Analyses}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

# General Information

In IRT analyses, person ability parameters as well as item difficulty
and, if applicable, discrimination parameters are estimated. Depending
on the available data format, a 1PL and 2PL analysis (only dichotomous
items) and, if applicable, additionally a PCM and GPCM analysis (also
polytomous items) are conducted, and the results are compared using
model fit.

The analyses should again only be conducted for all valid cases
(function argument `valid`). The 1PL and 2PL analyses must always be
conducted and use all dichotomously scored items (`select = "dich"`). If
the test also includes polytomous items, additional PCM and GPCM
analyses are performed using all items defined in the variable `mixed`.
If the item set is modified during the scaling process (e.g., because
items are excluded), the IRT analyses must be repeated with the updated
item set (in this case, the new analysis variables must be specified in
`select`, e.g. `dich_new` & `mixed_new`).

If a grouping exists (e.g., test booklets), the analyses are in most
cases conducted both for the full sample and for each group separately.
If the groups also share common items, additional IRT analyses are
conducted using only these common items. This can result in a large
number of IRT analyses (dichotomous and polytomous analyses for the full
sample and each group). In this case, the function
`grouped_irt_analysis()` can be used to perform IRT analyses for
multiple groups with a single command. Note that the data.frames `resp`
and `vars` must include the corresponding group variables and
group-specific analysis variables (see Section 4.3.2 Group Variables).

If not every person was administered every item, the argument
`missing_by_design` should be specified in both main functions by
providing the user-defined missing value for design-related missing
responses. This is necessary to correctly compute the number of persons
to whom an item was administered.

# Main function `irt_analysis`

The main function `irt_analysis()` automatically performs the required
IRT analyses, returns results in several tables and as text in the
console, and saves the (most important) results as Excel files and in
RDS format. ICC plots and Wright maps can also be generated and saved
(`plots = TRUE`). If the file names need to be modified (e.g., because a
test is scaled simultaneously for several cohorts), use the function
argument `name_group` that adds a suffix to each file name (e.g.,
`"cohort_6"`). The function automatically detects whether the item set
contains polytomous items and accordingly performs either a 1PL and 2PL
analysis (dichotomous items only) or a PCM and GPCM analysis (including
polytomous items). PCM and GPCM are estimated using the ConQuest
parameterisation `"item + item*step"`.

The function performs analyses for a single item set (e.g., all items
selected via the argument `select`). If IRT analyses are required for
multiple item sets (e.g., easy and difficult test booklets and common
items), but repeated calls to `irt_analysis()` should be avoided, the
function `grouped_irt_analysis()` can be used instead (see following
section).

Sometimes, the item parameters for the IRT analyses are already known
and need to be fixed to predetermined values. The function
`irt_analysis()` provides the possibility to use fixed item
difficulties. Because this function conducts two IRT analyses (1PL and
2PL models for dichotomous items, PCM and GPCM for polytomous or mixed
items), it contains two different function arguments: `xsi_fixed_1p` and
`xsi_fixed_2p`. The first argument may contain the fixed item
difficulties for the 1PL model or PCM, while the second argument may
contain the fixed item difficulties for the 2PL model or GPCM. Please
note that the item discrimination parameters from the 2PL model and GPCM
cannot be fixed within this package.

```{r}
# Rasch and 2PL
NEPSroutines::irt_analysis(
  resp = resp,
  vars = vars,
  select = "dich",
  valid = "valid",
  missing_by_design = -54,
  scoring = NULL,
  plots = TRUE,
  save = TRUE,
  print = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables",
  path_plots = "plots",
  overwrite = TRUE,
  digits = 3, 
  name_group = "all"
)

# PCM and GPCM
NEPSroutines::irt_analysis(
  resp = resp,
  vars = vars,
  select = "mixed",
  valid = "valid",
  scoring = "scoring",
  missing_by_design = -54,
  plots = TRUE,
  save = TRUE,
  print = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables",
  path_plots = "plots",
  suf_item_names = TRUE,
  overwrite = TRUE,
  digits = 3,
  name_group = "all"
)
```

Information on the individual function arguments can be obtained via the
help function (`?irt_analysis`).

# Main function `grouped_irt_analysis`

With the function `grouped_irt_analysis()` IRT analyses can be performed
for multiple item sets (e.g., easy and difficult test booklets and
common items) with a single command.

Although the function arguments are in principle the same as in
`irt_analysis()`, some arguments must now be specified per group. For
this purpose, a list is created in which each group corresponds to one
element. The names of the list elements correspond to the names of the
grouping variables (exactly as defined in `resp` and `vars`, e.g.,
`easy`). The list elements themselves contain the group-specific
argument values (e.g., `mixed_easy`).

In the case of the argument `select`, all groups must be included. For
other group-specific arguments (`control_tam`, `control_wle`,
`xsi_fixed_1p`, `xsi_fixed_2p`), list elements can be specified for only
some groups, or the entire argument can be left empty (`NULL`).

In the B129 study, there was a difficult and an easy test booklet that
also included common items. For the IRT analyses, it is therefore
important that the data.frames `resp` and `vars` include the logical
variables `easy`, `difficult`, and `common`, and that `vars`
additionally contains the group-specific analysis variables (see Section
4.3.2 Group Variables).

The function `grouped_irt_analysis` is defined as follows:

```{r}
# Rasch and 2PL
NEPSroutines::grouped_irt_analysis(
  resp = resp,
  vars = vars,
  valid = "valid",
  scoring = "scoring",
  missing_by_design = -54,
  select = c(easy = "dich_easy",
             difficult = "dich_diff",
             common = "dich_common"),
  overwrite = TRUE,
  plots = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables",
  path_plots = "plots"
)

# PCM and GPCM
NEPSroutines::grouped_irt_analysis(
  resp = resp,
  vars = vars,
  valid = "valid",
  scoring = "scoring",
  missing_by_design = -54,
  select = c(easy = "mixed_easy",
             difficult = "mixed_difficult",
             common = "mixed_common"),
  overwrite = TRUE,
  plots = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables",
  path_plots = "plots",
  suf_item_names = TRUE
)
```

# Minor Functions

In addition to the main function, the following minor functions can be
used:

| Function | Input | Output |
|-------------------|---------------------------|--------------------------|
| `irt_model` | Data.frames `resp` and `vars` containing information on responses, items, person characteristics, and optionally grouping | Results of the IRT analysis (R object, optionally RDS) |
| `icc_plots` | Output of the function `irt_model` | ICC plots for IRT models (PNG) |
| `wright_map` | Output of the function `irt_model` | Wright maps for IRT models (PNG) |
| `irt_summary` | Output of the function `irt_model` | Table with results of the IRT analysis (R object, optionally Excel) |
| `irt_model_fit` | Output of the function `irt_model` | Table with model fit for the 1PL and 2PL models or PCM and GPCM (R object, optionally Excel) |
| `step_analysis` | Output of the function `irt_model` (only for PCM analyses) | Table with results of the step analysis (R object, optionally Excel) |
| `print_irt_summary` | Output of the functions `irt_summary`, `irt_model`, and optionally `step_analysis` | Summary of the IRT and step analysis and additional results relevant for the Technical Report (printed in the console) |

Information on the individual function arguments can be obtained via the
help function (e.g. `?irt_summary`).
