---
title: "DIF Analyses"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{DIF Analyses}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

# General Information

Differential Item Functioning (DIF) refers to the situation in which an
item has different difficulty for different subgroups despite equal
ability. DIF analysis therefore ensures that no items systematically
favor or disadvantage particular groups (e.g., girls vs. boys or
migrants vs. non-migrants). A main-effect model and a DIF model are
estimated. The main effect represents the mean difference in competence
between two subgroups and is therefore not an indicator of DIF. Relevant
DIF is assumed when the effect size exceeds 0.4. If the value exceeds
0.6, the DIF is considered problematic; below this threshold it is only
considered potentially concerning. In addition, a Minimum Effects
Hypothesis Test is conducted to assess the magnitude of DIF. In this
framework, DIF effects should not be statistically significant. For NEPS
assessments, no DIF should be present (i.e., all values \< 0.4 and
non-significant).

The analyses should again only be conducted for all valid cases
(function argument `valid`). DIF analyses are based either on the 1PL
model or the PCM. As with IRT analyses, a dichotomous DIF analysis
should always be conducted. If the test also includes polytomous items,
an additional polytomous DIF analysis is performed. Grouping variables
generally do not need to be considered in DIF analyses, as they are
already incorporated as DIF variables in the model.

# Main Function

To test whether DIF is present, the function `dif_analysis()` can be
used. It can perform DIF analyses for multiple DIF variables
simultaneously (defined in the argument `dif_vars`). In this case, the
argument `select` can either contain a vector specifying a separate
select variable for each DIF variable (see example), or—if the item set
does not vary across DIF variables—a single string can be used as usual
(e.g., `select = "mixed"`). The required items may vary when only
specific items are considered for a given DIF variable (e.g., only
common items across test booklets for the DIF variable `difficulty`).

The function tests whether item difficulties differ significantly
between DIF groups and also performs a model comparison between the DIF
model and the main-effect model using AIC and BIC. The results are
automatically saved in RDS format and as Excel tables. In particular,
the function produces a table that can be directly used for the
Technical Report (TR). This table reports unstandardized (before
parentheses) and standardized (in parentheses) DIF effects for each
item. If the file names need to be modified (e.g., because a test is
scaled simultaneously for several cohorts), use the function argument
`name_group` that adds a suffix to each file name (e.g., `"cohort_6"`).
A summary of the results is also printed to the console.

```{r}
# For Rasch
NEPSroutines::dif_analysis(
  resp = resp,
  vars = vars,
  select = c("dich_common", "dich", "dich"),
  valid = "valid", 
  dif_vars = c("difficulty", "sex", "migration"),
  overwrite = TRUE,
  print = TRUE,
  save = TRUE,
  return = FALSE,
  path_table = "tables",
  path_results = "results"
)

# For PCM
NEPSroutines::dif_analysis(
  resp = resp,
  vars = vars,
  select = c("mixed_common", "mixed", "mixed"),
  valid = "valid", 
  dif_vars = c("difficulty", "sex", "migration"),
  scoring = "scoring", 
  overwrite = TRUE,
  print = TRUE,
  save = TRUE,
  return = FALSE,
  path_table = "tables",
  path_results = "results",
  suf_item_names = TRUE
)
```

Information on the individual function arguments can be obtained via the
help function (`?dif_analysis`).

# Minor Functions

In addition to the main function, the following Minor functions can be
used. Note that some functions are intended only for DIF analyses with a
single DIF variable, while others can also be used for DIF analyses with
multiple DIF variables. Accordingly, the function argument for the DIF
variable(s) is either `dif_var` (for a single DIF variable) or
`dif_vars` (for multiple DIF variables). The argument `select` can
therefore be specified either as a string or as a vector (i.e., one
`select` variable per DIF variable).

| Function | Input | Output |
|----|----|----|
| `dif_model` | Data.frames `resp` and `vars` containing information on responses, items, and person characteristics | Results of the DIF analysis for a single DIF variable (R object) |
| `conduct_dif_analysis` | Data.frames `resp` and `vars` containing information on responses, items, and person characteristics | Results of the DIF analysis for multiple DIF variables (R object, optionally RDS) |
| `dif_summary` | Output of the function `dif_model` (or the element `models$NameDIFVariable` from the output of `dif_analysis`) | Tables with results of the DIF analysis for a single DIF variable (R object, optionally Excel) |
| `summarize_dif_analysis` | Output of the function `conduct_dif_analysis` (or the element `models` from the output of `dif_analysis`) | Tables with results of the DIF analyses for multiple DIF variables (R object, optionally Excel) |
| `build_dif_tr_tables` | Output of the function `dif_summaries` | Table with results for the Technical Report (R object, optionally Excel) |

Information on the individual function arguments can be obtained via the
help function (e.g., `?dif_summary`).
