---
title: "Getting Started"
author: "Jana Welling"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

\newpage

## Welcome to NEPSroutines

Welcome to **NEPSroutines**. This package provides functions for preparing, scaling, and scoring NEPS competence data.

This guide serves as an overview of the available documentation and helps you navigate the package.

## Documentation with Vignettes

Information on the scaling procedure, working with R and R Markdown, NEPS data, and the NEPSroutines package are documented using **vignettes**.

To find all available vignettes included in this package, use the following R code:

```{r, eval = FALSE}
utils::vignette(package = "NEPSroutines")
```

To open a specific vignette, replace `"my_vignette"` with the required vignette name:

```{r, eval = FALSE}
utils::vignette("my_vignette", package = "NEPSroutines")
```

## Available Documentation

The package documentation is organized according to the typical scaling process. The following sections list all available vignettes.

### Introduction to R and Scaling NEPS Data

If you are new to scaling NEPS data and maybe also to using R, start by reading the first vignettes that give you a short introduction to the scaling of NEPS data using R, RStudio, and R Markdown.

-   *scaling_NEPS_data*

-   *scaling_with_R*

### Introduction to NEPSroutines

Get acquainted with the NEPSroutines package, its required data structure, and the package workflow.

-   *package_introduction*

### Data Import and Preparation

Learn how to prepare competence items, score items, define missing values, and create the required data structures.

-   *import_data*
-   *prepare_data*

### Descriptive Analyses

Obtain descriptive statistics for samples, items, and test booklets.

-   *descriptive_analyses*

### Missing Value Analyses

Analyze user-defined missing values at the person and item level.

-   *missing_values_analyses*

### Psychometric Analyses

Evaluate item and test quality.

-   *irt_analyses*
-   *dif_analyses*
-   *distractor_analyses*
-   *dimensionality_analyses*

### Score Creation and SUF Generation

Estimate scores and create the Scientific Use File.

-   *create_scores*
-   *create_suf*

### Technical Report

The package supports the half-automated creation of the Technical Report.

-   *technical_report*

## Further Information

For details on individual functions, see the corresponding help pages, e.g.

```{r, eval = FALSE}
?irt_analysis
?create_scores
```

If the package and function documentation is missing vital information or if you are stuck, please write to *skalierung\@lifbi.de*.
