---
title: "Getting Started"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Getting Started}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

\newpage

## Welcome to NEPSroutines

Welcome to **NEPSroutines**. This package provides functions for preparing, scaling, and scoring NEPS competence data.

This guide serves as an overview of the available documentation and helps you navigate the package.

## Documentation with Vignettes

Information on the scaling procedure, working with R and R Markdown, NEPS data, and the NEPSroutines package are documented using **vignettes**.

To find all available vignettes included in this package, use the following R code:

```{r, eval = FALSE}
utils::vignette(package = "NEPSroutines")
```

To open a specific vignette, replace `"my_vignette"` with the required vignette name:

```{r, eval = FALSE}
utils::vignette("my_vignette", package = "NEPSroutines")
```

The following vignettes are included in the package:

```{r, echo = FALSE, results = 'asis'}
vignettes <- utils::vignette(package = "NEPSroutines")
cat(paste0("- ", vignettes$results[, "Item"], "\n"), sep = "")
```

## Available Documentation

The package documentation is organized according to the typical scaling process.

### Introduction to R and Scaling NEPS Data

If you are new to scaling NEPS data and maybe also to using R, start by reading the first vignettes that give you a short introduction to the scaling of NEPS data using R, RStudio, and R Markdown.

-   *Scaling NEPS data*

-   *Scaling with R*

### Introduction to NEPSroutines

Get acquainted with the NEPSroutines package, its required data structure, and the package workflow.

-   *Package Introduction*

### Data Import and Preparation

Learn how to prepare competence items, score items, define missing values, and create the required data structures.

-   *Import Data*
-   *Prepare Data*

### Descriptive Analyses

Obtain descriptive statistics for samples, items, and test booklets.

-   *Descriptive Analysis*

### Missing Value Analyses

Analyze user-defined missing values at the person and item level.

-   *Missing Responses per Person*
-   *Missing Responses per Item*

### Psychometric Analyses

Evaluate item and test quality.

-   *Item Response Theory Analysis*
-   *Differential Item Functioning Analysis*
-   *Distractor Analysis*
-   *Dimensionality Analysis*

### Score Creation and SUF Generation

Estimate scores and create the Scientific Use File.

-   *Create Scores*
-   *Create SUF*

## Further Information

For details on individual functions, see the corresponding help pages, e.g.

```{r, eval = FALSE}
?irt_analysis
?create_scores
```

If the package and function documentation is missing vital information or if you are stuck, please write to *skalierung\@lifbi.de*.
