---
title: "Descriptive Analyses"
author: "Jana Welling, Christian Diegel"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Descriptive Analyses}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

## Analysis of the Whole Sample

First, descriptive analyses of the sample should be conducted. Within
the NEPSroutines package, several smaller functions are available for
this purpose. They summarize key information using text and tables and
display the results in the console.

The following table provides an overview of the available functions:

| Function | Output |
|----|----|
| `n_valid` | Number of all valid and invalid cases in the dataset. |
| `desc_con` | Table with descriptive statistics (e.g., mean, SD) for the continuous variables defined in `desc`. |
| `desc_abs` | Table with the number of cases in each category for the categorical variables defined in `desc` (e.g., number of males and females in the dataset for the variable `sex`). |
| `desc_perc` | Table with percentage values for each category of the categorical variables defined in `desc` (e.g., percentage of males and females in the dataset for the variable `sex`). The function argument `useNA` allows specifying whether missing cases should be included in the percentage calculations (`TRUE`) or not (`FALSE`). |
| `desc_nom` | Combines the two functions `desc_abs` and `desc_perc`. It therefore provides both absolute and relative frequencies for categorical variables in a single table. |
| `show_attributes` | Displays variable labels, allowing values to be assigned to their corresponding categories (e.g., 1 = male and 2 = female). This function only works if the variables are defined as `hvn_lbl`. |

Most of these functions use two new function arguments. The argument
`resp` requires a dataset containing sociodemographic information for
all participants. If the data have been prepared as suggested in this
guide, this corresponds to the dataset `resp`. The argument `desc`
requires the name(s) of the variables to be analyzed, for example all
categorical sociodemographic variables for the function `desc_nom`.

The corresponding syntax could look as follows:

```{r}
# Sample size
message("There are in total ", nrow(resp), " cases in the dataset.")

# Number of (in)valid cases
NEPSroutines::n_valid(resp = resp, valid = "valid")

## Descriptives (mean, sd, etc.) of continuous variables
NEPSroutines::desc_con(resp = resp, desc = "age", valid = "valid")

# Creating vectors with all categorical sociodemographic or booklet variables, respectively
sociodemographics = c("sex", "attendsGymnasium", "migration", "books")
booklet = "difficulty" # In other NEPSroutiness some more characteristics might apply here, e.g. position of booklet

# Descriptives (attributes, frequency) of nominal sociodemographic variables
NEPSroutines::desc_nom(resp = resp, desc = sociodemographics, valid = "valid")
NEPSroutines::show_attributes(resp = resp, desc = sociodemographics)

# Descriptives (attributes, frequency) of nominal booklet variables
NEPSroutines::desc_nom(resp = resp, desc = booklet, valid = "valid")
NEPSroutines::show_attributes(resp = resp, desc = booklet)

# Delete variables
rm(sociodemographics, booklet)
```

Information on the individual function arguments can be obtained via the
help function (e.g., `?desc_nom`).

## Analysis by Subgroup (if applicable)

In many scaling applications, one or more grouping variables are present
(e.g., different test booklets). It is useful to report sample size as
well as the number and type of items separately for these groups. In
particular, descriptive statistics for all dimensionality variables
(i.e., those later used in the dimensionality analysis) should be
examined separately by group. This information is also required for the
Technical Report. The NEPSroutines package provides two functions for
descriptive analysis by test booklet: `sample_by_group()` and
`props_by_group()`.

The function `sample_by_group()` returns a table with the sample size
per group. The argument `grouping_variable` specifies the name of the
grouping variable in `resp`. The argument `labels` is optional and can
be used to assign names to groups if the corresponding variable in
`resp` does not already contain labels. For this purpose, a named vector
is provided, where the names correspond to the group names (see example
code).

The function `props_by_group()` returns a table describing item
properties per group, for example how many items of each type are
included in each group. The argument `properties` requires a character
vector containing the names of all variables in `vars` that describe
item characteristics (e.g., `text_type`, `kog_type`, and `type`). In
addition, user-defined labels for categories can be provided via the
argument `labels` if the corresponding variables in `vars` are not
already labelled.

The syntax could look as follows:

```{r}
# Sample size by test version
NEPSroutines::sample_by_group(
  resp,
  grouping_variable = "difficulty",
  labels = c("EasyTestlet" = 0, "DifficultTestlet" = 1),
  save = TRUE,
  overwrite = TRUE,
  path = "tables"
)

# Testlet properties by test version
lbls_txt = c(Advertising = 1, Information = 2, Instruction = 3, Literary = 4, Commenting = 5)
lbls_kog = c(Finding_information = 1, Drawing_conclusions = 2, Reflecting = 3)
lbls_type = c(MC = 2, CMC = 1, TXT = 3)

NEPSroutines::props_by_group(
  vars,
  select = "mixed",
  grouping = c("easy", "difficult"),
  properties = c("text_type", "kog_type", "type"),
  labels = list(text_type = lbls_txt, kog_type = lbls_kog, type = lbls_type),
  save = TRUE, overwrite = TRUE,
  path = "tables"
)

# Delete variables
rm(lbls_txt, lbls_kog, lbls_type)
```

Information on the individual function arguments can be obtained via the
help function (e.g., ?`props_by_group`).
