---
title: "Example Data and Scripts"
author: "Jana Welling"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Example Data and Scripts}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

To help you getting started with scaling using `NEPSroutines`, the
package provides example data and scripts. 

## Example data

`NEPSroutines` contains example data sets that correspond to different test designs.
In the current package version, this includes:

- `dat1`: The simulated data includes a linear test with 1000
  persons, 15 items (all MC), no rotation or booklet design, and no
  dimensionality variable.

- `dat2`: The simulated data includes a linear test with 1500
  persons, 17 items (9 MC, 4 SCR, 4 CMC), a rotation design, the
  dimensionality variable "content", and no booklet design.

- `dat3`: The simulated data includes a linear test with 2100
  persons, 21 items (16 MC, 5 CMC), a rotation design, the
  dimensionality variable "texttype", and three booklets "easy",
  "medium", and "difficult".

- `dat4`: The simulated data includes a multi-stage test with three
  stages, 3400 persons, 34 items (26 MC, 8 CMC), a rotation design, and
  the dimensionality variable "component".
  
You can access the data while `NEPSroutines` is loaded in your R environment.

To load the data into your current environment, type: 

```{r}
data("dat1") # for loading dat1
data("dat2") # for loading dat2
data("dat3") # for loading dat3
data("dat4") # for loading dat4
```

## Example scripts 

For each data set, an example scaling script in RMD (R Markdown) format
and its HTML output reporting the results are available. Please note that
the example scripts don't include data preparation in this package
version. 

You can get a list of all available scripts and outputs with:

```{r}
directory <- system.file("examples", package = "NEPSroutines")
list.files(directory)
```

You can access RMD files using:

```{r}
file.edit(system.file("examples", "my_file.Rmd", package = "NEPSroutines"))
```

And access HTML files using:

```{r}
browseURL(system.file("examples", "my_file.html", package = "NEPSroutines"))

```
