---
title: "Missing Values Analyses"
author: "Jana Welling, Christian Diegel"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Missing Values Analyses}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

## General Information

For scaling a test, it is important to analyse the different types of
missing values, i.e. to examine the reasons for missing responses and
how often they occur. For NEPS tests, this is done both per person (how
many items were not answered on average per person and for what reason)
and per item (how many persons answered or did not answer an item and
for what reason). To conduct these analyses, missing values of the
competency items must be coded as user-defined missing values. Which
values are typically used in NEPS and how to create the function
arguments `mvs` and `labels_mvs` is described in Section *User-Defined
Missing Values* in vignette `prepare_data`.

The analyses should only be conducted for all valid cases (function
argument `valid`). Only those items that are also used for the final IRT
scaling should be considered (provided in function argument `select`; in
most cases `dich` or `mixed`, depending on the composition of the item
set). The results of the analyses are automatically saved in RDS format.
The summary of the results is saved as an Excel file and printed to the
console. To generate and save plots, the function argument `plots` must
be set to `TRUE`. If the file names need to be modified (e.g., because a
test is scaled simultaneously for several cohorts), use the function
argument `name_group` that adds a suffix to each file name (e.g.,
`"cohort_6"`).

## Analysis of Missing Values per Person

### Main Function

The function `mv_person()` is used to analyse missing values per person.
This analysis includes information on all user-defined missing values
specified in the argument `mvs`. In addition, statistics are also
computed for all missing values jointly defined in `mvs`. Missing values
not included in `mvs` are not included in this sum. It is therefore
important to include all existing user-defined missing values in `mvs`
if the aggregate value (“ALL”) is to be meaningfully interpreted. An
exception are design-related missing responses, which are automatically
excluded from the dataset prior to the analysis. For this purpose, the
corresponding user-defined missing value must be specified in the
argument `missing_by_design` (default is `-54`). It is very important to
specify the correct value here, otherwise incorrect responses will be
filtered out and the number of persons to whom each item was
administered will also be incorrect.

The analyses can also be conducted separately for different groups
(e.g., test booklets). These must be defined in the argument `grouping`.
Missing values are then calculated per group only for the items that
were also administered to that group. The name of the grouping (e.g.,
“test version”) can be specified using the argument `name_grouping` for
labelling the plots. If results are required not only by group but also
for the total sample (both in tables and plots), the argument `show_all`
must be set to `TRUE`.

If the analyses are conducted for a multistage test, the function
argument `stages` needs to be defined. This argument is a named numeric
vector which contains for each stage as vector element the number of
items per stage and as name of the vector element the name of the stage
variable as name. For example, if the test consisted of two stages with
10 items in the first and 8 items in the second stage, the argument
should be `stages = c(stage1 = 10, stage2 = 8)`.

```{r}
NEPSroutines::mv_person(
  resp = resp,
  vars = vars,
  select = "mixed",
  valid = "valid",
  grouping = c("easy", "difficult"),
  mvs = mvs,
  labels_mvs = labels_mvs,
  missing_by_design = -54,
  plots = TRUE,
  print = TRUE,
  save = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables",
  path_plots = "plots/missings_by_person",
  show_all = FALSE,
  overwrite = TRUE,
  name_grouping = "test version",
  digits = 3
)
```

Information on the individual function arguments can be obtained via the
help function (`?mvp_analysis`).

### Minor Functions

In addition to the main function, the following minor functions can be
used:

| Function | Input | Output |
|------------------------|------------------------|------------------------|
| `mvp_analysis` | Data.frames `resp` and `vars` containing information on responses, items, person characteristics, and optionally grouping | Results of the MVP analyses (R object, optionally RDS) |
| `mvp_plots` | Output of the function `mvp_analysis` or the element `mv_p` from the output of `mv_person` | Plots for each user-defined missing value type (PNG) |
| `mvp_table` | Output of the function `mvp_analysis` or the element `mv_p` from the output of `mv_person` | Table with results of the MVP analyses for the Technical Report (R object, optionally Excel) |
| `print _mvp_results` | Output of the function `mvp_analysis` or the element `mv_p` from the output of `mv_person` | Summary of the MVP analysis results (printed in the console) |

Information on the individual function arguments can be obtained via the
help function (`?mvp_analysis`).

## Analysis of Missing Values per Item

### Main function

Similar to the function `mv_person()`, missing values can also be
analysed using the function `mv_item()`. The difference compared to the
function described above is that the proportions of specific missing
values are now displayed for each item rather than per person.
Information is again provided for all user-defined missing values
specified in the argument `mvs`. As before, statistics are also computed
for all missing values jointly defined in `mvs`. Missing values not
included in `mvs` are not considered in this sum. It is therefore
important to include all existing user-defined missing values in `mvs`
if the aggregated value (“ALL”) is to be meaningfully interpreted. An
exception are design-related missing responses, which are automatically
excluded from the dataset prior to the analysis. For this purpose, the
corresponding user-defined missing value must be specified in the
argument `missing_by_design` (default is `-54`). It is very important to
specify the correct value here; otherwise, incorrect responses will be
filtered out and the number of persons to whom each item was
administered will also be incorrect.

The analyses can also be conducted separately for different groups
(e.g., test booklets). These must be defined in the argument `grouping`.
Missing values are then calculated per group only for the items that
were administered to that group. The name of the grouping (e.g., “test
version”) can be specified using the argument `name_grouping` for
labelling the plots. Missing values per item are displayed depending on
item position and, if applicable, grouping.

If the analyses are conducted for a multistage test, the function
argument `stages` needs to be defined. The argument is a character
vector which contains the names of stage variables in `resp` and `vars`.
For example, if the test consisted of three stages, three logical
variables that indicate if a person reached stage X or an item was part
of stage X need to be defined in `resp` and `vars`, respectively (e.g.,
named `"stage1"`, etc.). The function argument would then be defined as
`stages = c("stage1", "stage2", "stage3")`. Note that the variables need
to be identically named in `resp` and `vars`.

By setting the argument `save` to `TRUE`, results can be saved in `.rds`
and `.xlsx` files. The results from the Excel file can, for example, be
used in the Technical Report. If the argument `suf_item_names` is set to
`TRUE`, the names of polytomous items with collapsed categories are
displayed without the suffix `"_collapsed"`. By default
(`suf_item_names = FALSE`), item names remain unchanged. Note that in
`.rds` files, item names always remain unchanged.

```{r}
NEPSroutines::mv_item(
  resp = resp,
  vars = vars,
  select = "mixed",
  valid = "valid",
  grouping = c("easy", "difficult"),
  mvs = mvs,
  labels_mvs = labels_mvs,
  missing_by_design = -54,
  position = c(easy = "position_easy_mixed",
               difficult = "position_difficult_mixed"),
  plots = TRUE,
  print = TRUE,
  save = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables",
  path_plots = "plots/missings_by_item",
  suf_item_names = TRUE,
  show_all = FALSE,
  overwrite = TRUE,
  name_grouping = "test version",
  digits = 3
)
```

Information on the individual function arguments can be obtained via the
help function (`?mvi_analysis`).

### Minor Functions

In addition to the main function, the following minor functions can be
used:

| Function | Input | Output |
|------------------------|------------------------|------------------------|
| `mvi_analysis` | Data.frames `resp` and `vars` containing information on responses, items, person characteristics, and optionally grouping | Results of the MVI analyses (R object, optionally RDS) |
| `mvi_plots` | Output of the function `mvi_analysis` (or element `mv_i` from the output of `mv_item`) | Plots for each user-defined missing value type (PNG) |
| `mvi_table` | Output of the function `mvi_analysis` (or element `mv_i` from the output of `mv_item`) | Table with results of the MVI analyses for the Technical Report (R object, optionally Excel) |
| `print_mvi_results` | Output of the function `mvi_analysis` (or element `mv_i` from the output of `mv_item`) | Summary of the MVI analysis results (printed in the console) |

Information on the individual function arguments can be obtained via the
help function (e.g., `?mvi_analysis`).
