---
title: "Data Preparation"
author: "Jana Welling, Christian Diegel"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
    toc: true
    number_sections: no
  bookdown::pdf_document2:
    toc: true
    number_sections: no
bibliography: ../inst/NEPSroutines.bib
vignette: >
  %\VignetteIndexEntry{Data Preparation}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>"
)

```

\newpage

## Prepare Competence Data

### Dichotomous Item Scoring

In the next step, the unscored items must be scored. For each item, a
new variable is created indicating whether the item was answered
correctly (`1`) or incorrectly (`0`). The function
`dichotomous_scoring()` can be used for this purpose. The function takes
the data.frames `resp` and `vars` as input, along with the character
vector `old_names` containing the names of the unscored items. In
principle, the character vector `new_names` with the desired names for
the scored items can also be passed to the function. However, if the
scaling is performed for a NEPS study, this is not necessary because the
NEPS naming convention (name of the unscored item + suffix `"_c"`) is
implemented as the default in the function. For the function to work,
the variable `correct_response` must be defined in `vars`. If more than
one response option can be correct for an item, pass the punctuation
mark used to separate the correct responses in this variable to the
function argument `sep` as a character string (see Section *Dataset
`vars`* in vignette `package_introduction`, default is `";"`). The
function extends the data.frame `resp` with the new items.

```{r}
resp <- NEPSroutines::dichotomous_scoring(resp, vars, old_names = item_names) 
```

In the NEPSroutines package, it is necessary to create a separate row in
the data.frame `vars` for each version of an item (e.g., unscored,
scored). Since most information is identical between unscored and scored
items, the function `duplicate_items()` can be used for this purpose.
This function duplicates the item information for any number of items
and only applies explicitly requested modifications (e.g., item name).
The function takes the data.frame `vars`, the character vector
`old_names` with the names of the original items, the character vector
`new_names` with the names of the new items, and optionally the list
`change` if information other than the item names should also be
modified. The name of each list element corresponds to the name of the
variable that differs between the old and new items. The content of each
list element is either a single value used for all new items or a vector
containing one value per new item. The function returns the data.frame
`vars` including the new items. Since only the variables `raw` and
`dich` should differ between the unscored and scored items, the function
call looks as follows.

```{r}
vars <- NEPSroutines::duplicate_items(
  vars,
  old_names = item_names,
  new_names = paste0(item_names, "_c"),
  change = list(raw = FALSE, dich = TRUE)
)
```

### Polytomous Item Scoring

If the competency test contains polytomous items, these must also be
scored. The function `pc_scoring()` can be used for this purpose. The
function takes the data.frame `resp` and the list `poly_items` as input,
with one element per polytomous item. The names of the elements
correspond to the names of the polytomous items, and each element
contains a character vector with the names of all subitems. In NEPS, the
name of a polytomous item generally consists of the names of the
subitems. Only the digit that differs between the items is replaced with
an `"s"`. The function extends the data.frame `resp` with the new items.

Before scoring, the function `pc_scoring()` performs an imputation of
missing values on the subitems of polytomous items by default—provided
that at least 50% of the subitems of a polytomous item contain valid
responses. This functionality is enabled by default through the
arguments `impute = TRUE` and `threshold = .50`. The imputation is based
on a Rasch model: using the estimated item and person parameters (EAP
values), the probability of solving each subitem is calculated for each
person, and an individual response is predicted from this. The arguments
`vars` and `select` are required for the imputation. `vars` refers to a
dataset containing information about the competency items. With the
argument `select`, a logical variable within `vars` is specified that
identifies all scored dichotomous items (e.g., `select = "dich"`). This
includes both multiple-choice items and subitems of polytomous items.
The imputed values are used exclusively for scoring the polytomous
items. In the returned dataset, the original (non-imputed) subitem
responses remain unchanged. Information on the imputation is
automatically saved in Excel and RDS format.

```{r}
poly_items <- list(
  Item1s_c = paste0("Item1", c(1:3), "_c"),
  Item2s_c = paste0("Item2", c(1:4), "_c"),
  etc. 
) 
resp <- NEPSroutines::pc_scoring(
  resp,
  poly_items = poly_items,
  vars = vars,
  select = "dich"
)
```

As with dichotomous item scoring, the polytomous items must also be
stored in the data.frame `vars`. This can again be accomplished using
the function `duplicate_items()`. One subitem is used as the reference
item in each case.

```{r}
first_subitem <- sapply(poly_items, function(x) x[1])
vars <- NEPSroutines::duplicate_items(
  vars,
  old_names = first_subitem,
  new_names = names(poly_items),
  change = list(raw = FALSE, dich = FALSE, poly = TRUE) 
)
```

If individual PCM categories are sparsely populated, i.e., if the cell
frequency in a frequency table falls below a certain value (200 in
NEPS), they must be merged with the next lower category. If, for
example, category 0 is too sparsely populated, it is merged with the
next higher category accordingly. The function
`collapse_response_categories()` checks this condition and automatically
performs the merging if necessary. The function takes the data.frame
`resp` and, via `select`, the name of the variable in `vars` that
identifies all polytomous items. The default threshold for sparse cell
frequencies is 200 but can be changed using the function argument
`per_cat`. The function returns the data.frame `resp`, which contains
all original variables and, additionally, all collapsed items. This
means that for each item with sparse response categories, there are now
two variables in the dataset—the original item and a new item with
collapsed response categories. The names of the new items end with the
suffix `_collapsed`. The function returns a list of all modified items
in the console. If `save = TRUE`, this list is also saved as an Excel
table. In the rare case that collapsing would leave an item with fewer
than two categories, the function refrains from collapsing and issues a
warning containing the name of the item in the console. Such an item
should then be collapsed manually. Remember that the names of manually
collapsed items should also be added to the list of collapsed items.

```{r}
resp <- NEPSroutines::collapse_response_categories(resp, vars, select = "poly")
```

If items were collapsed, the new items must be stored in the data.frame
`vars`. The names of the old items (with the suffix `_c`) and the new,
collapsed items (with the suffix `_collapsed`) can be obtained from the
console output or the Excel table. The function `duplicate_items()` can
again be used for this purpose. Note that the new items are also stored
as polytomous items (`poly = TRUE`) even if they only contain two
response categories.

```{r}
original_items <- c("original.item_1", "original.item_2")
collapsed_items <- c("collapsed.item_1", "collapsed.item_2")
vars <- NEPSroutines::duplicate_items(
  vars,
  old_names = original_items,
  new_names = collapsed_items
)
```

If a competency test contains both simple and polytomous items, most of
the scaling is performed using the item set consisting of the polytomous
items and the simple scored items. However, the subitems of the
polytomous items are not used. To enable the use of this item set in the
subsequent analyses, a logical variable is now created that identifies
the corresponding items. In our example, this variable is called
`mixed`. Note that items for which a collapsed item was created should
be excluded from the analyses.

```{r}
vars$mixed <- ifelse(
  vars$poly,
  TRUE,
  ifelse(vars$dich & !vars$item %in% unlist(poly_items), TRUE, FALSE)
) 
vars$mixed[vars$item %in% original_items] <- FALSE
```

After combining the polytomous items, the item positions now contain
gaps (e.g., if subitems 1 to 4 previously occupied positions 1 to 4,
only a single polytomous item remains at position 1 afterward).
Therefore, a new position variable without gaps should be created for
each group. This can be accomplished using the function `pos_new()`. The
function takes `vars`, `items`, and the (named) character vector
`position` as input. If there are multiple groups, `position` contains
the names of the group-specific position variables (the names of the
vector elements correspond to the names of the grouping variables); if
there is only one group, it contains the name of the single position
variable. The function returns the data.frame `vars` with the new
position variables.

```{r}
vars <- NEPSroutines::pos_new(
  vars,
  select = "mixed",
  position = c(easy = "position_easy", difficult = "position_difficult")
)
```

Finally, the scoring variable `scoring` must be created, which is
required for polytomous IRT and DIF analyses. By default, dichotomous
items in NEPS are scored with `1` and polytomous items with `0.5`. Items
that are actually polytomous but became dichotomous through collapsing
response categories are also scored with `1`. However, this can be
adjusted in individual cases.

```{r}
vars$scoring[vars$mixed] <- ifelse(
  apply(resp[ , vars$item[vars$mixed]], 2, max, na.rm = TRUE) > 1,
  0.5,
  1
)
```

### User-Defined Missing Values

The competency items in NEPS contain so-called user-defined missing
values (UDMV). Missing values are therefore coded using negative
integers to distinguish between different types of missing values. In
NEPS, the following UDMVs exist:

-   `-99`: filtered

-   `-97`: omitted (OM)

-   `-95`: not valid (NV)

-   `-94`: not reached (NR)

-   `-93`: not applicable

-   `-91`: test aborted (TA)

-   `-90`: missing without specified reason (UM)

-   `-56`: not participated

-   `-55`: not determinable (ND)

-   `-54`: missing by design (MD)

-   `-22`: skipped

-   `-21`: response reset (AZ)

Not every type of missing value occurs in every competency test. For
scaling, one should therefore first check which types are actually
present. This can be done using the `table` function.

```{r}
table(unlist(resp[ , vars$item]))
```

The existing UDMVs are now defined in a named integer vector. The
missing values can be named arbitrarily, but abbreviations are usually
the most practical. For example:

```{r}
mvs = c(OM = -97, NV = -95, NR = -94, ND = -55, MD = -54)
```

The labels of the UDMVs are now stored in a named character vector.
These labels are later used as captions and headings in plots and
tables. The names must correspond to the names of the previously defined
named integer vector. Note that the additional element `"ALL"` with the
label for all missing values is required here.

```{r}
labels_mvs = c(
  ALL = "total missing items",
  OM = "omitted items",
  NV = "not valid items",
  NR = "not reached items",
  ND = "not determinable items",
  MD = "items missing by design"
)
```

## Prepare DIF Variables

### Calculate Age

In NEPS, age is usually not available directly and must first be
calculated from the date of birth and the assessment date. This is done
using the function `calculate_age()`. The function takes the data.frame
`resp` and the names of the variables containing the date of birth
(year, month, and day) as input. For the test date variables, one can
either provide the names of the corresponding variables in `resp` (if
persons were tested on different dates) or alternatively specify a
single number for each component (if all persons were tested in the same
year/month/day). Specifying the birth year and month as well as the test
year and month is mandatory, whereas the birth day and test day may be
omitted. In this case, the function uses the 15th day of the month as
the default. The function returns a vector containing age in years.

```{r}
resp$age <- NEPSroutines::calculate_age(
  resp,
  birth_year = "birthy",
  birth_month = "birthm",
  birth_day = "birthd",
  test_year = 2022,
  test_month = 10,
  test_day = 17
)
```

### Dichotomize Sociodemographic Variables

Some DIF variables (e.g., age) still have more than two categories and
therefore need to be dichotomized. The split criteria for
dichotomization are:

-   **School type**: non-academic secondary school (`0`) / academic
    secondary school (`1`)

-   **School-leaving qualification**: no university entrance
    qualification (`0`) / university entrance qualification (`1`)

-   **Migration background**: \> 2.25 generation (`0`) / 1st to 2nd
    generation (`1`)

-   **Number of books**: \< 100 books (`0`) / ≥ 100 books (`1`)

-   **Age**: e.g., median split (only necessary for age-heterogeneous
    groups)

Dichotomization can conveniently be performed using the `ifelse()`
function. For example:

```{r}
resp$migration <- ifelse(
  resp$migration %in% c(0, 4:10),
  0,
  ifelse(is.na(resp$migration), NA, 1)
)
```

### Create Variable for Test Booklet Design

The test booklet design variable from the raw data cannot yet be used
directly. First, the necessary information must be extracted from it
(see Section *Test Booklet Design Information* in vignette
`import_data`): Were there different rotations of the test booklets?
Were there different versions of the test booklets? Was there any other
information relevant for scaling? For each piece of information relevant
to the DIF analyses, a dichotomous variable is created in the dataset
`resp`. If the IRT models are additionally to be estimated separately
for different groups (especially for different test booklets), a logical
variable is also created for each group indicating whether a person
belongs to that group. For example, the B129 study contains an easy and
a difficult test booklet.

```{r}
# Create design variable for testlet version
resp$testlet <- ifelse(resp[[design]] %in% c(241, 242, 243, 244, ...), "A", "B")  

# Create logical variables for testlet version
resp$easy <- ifelse(resp$testlet == "A", TRUE, FALSE)
resp$difficult <- ifelse(resp$testlet == "B", TRUE, FALSE)
```

### Assign Labels for Variables

To avoid confusion regarding the values of the dichotomous DIF
variables, labels should be assigned to the variables. This can be done
very easily using the function `labelled()`. For example, the code for
the migration background variable is as follows:

```{r}
resp$migration <- haven::labelled(
  resp$migration,
  c("no migration background" = 0, "migration background" = 1)
)
```

## Other Preparations

### Identify Valid Cases

If respondents have provided only very few valid responses, they are
considered invalid cases and are excluded from the analyses. In NEPS,
the minimum number of valid responses is set to three by default. To
identify (in)valid cases, a new logical variable is created in `resp`
using the function `min_val()`. The function takes `resp`, `vars`, and
`select` as input. Under `select`, one should specify the variable that
identifies all items to be used for scaling (i.e., `dich` for a purely
dichotomous item set and `mixed` for a mixed item set). In addition, the
minimum number of valid responses can be defined using the argument
`min.val` (default is 3), and a vector containing all values to be
treated as invalid can be specified using the argument `invalid`
(default is all negative values and `NA`s). The function returns a
logical vector (`TRUE` for all valid cases). Note that if the item set
is modified (e.g., because some items were excluded), it may be
necessary to create a new valid variable (e.g., `valid_new`).

```{r}
resp$valid <- NEPSroutines::min_val(resp, vars, select = "mixed")
```

### Create Group Variables

If a grouping exists (e.g., test booklets), additional variables must be
created. This section assumes that both `vars` and `resp` already
contain a logical variable for each group that identifies the items or
persons belonging to the respective group (e.g., `easy` and
`difficult`).

If the groups were administered not only different items, IRT analyses
are performed, among others, for all common items. For this purpose, a
logical variable must be created in `vars` indicating which items were
administered to all groups. Analogously, a logical variable must be
created in `resp` indicating which persons were administered the common
items. Since the common items were administered to all groups, they were
naturally administered to all persons as well (the variable is therefore
`TRUE` for all persons). In our example, the variables are both called
`common`.

```{r}
vars$common <- vars$easy & vars$difficult
resp$common <- TRUE
```

In the case of grouping, group-specific analysis variables (e.g.,
`dich`, `mixed`) must also be defined in the dataset `vars` for each
group. For example, if there is an easy and a difficult test booklet
with partially overlapping items, a new version of each required
analysis variable should be created that identifies only the items
relevant to that group. The `mixed` variables only need to be created if
the test contains polytomous items.

```{r}
# New dich variables
vars$dich_easy <- vars$dich & vars$easy
vars$dich_difficult <- vars$dich & vars$difficult
vars$dich_common <- vars$dich & vars$common 

# New mixed variables
vars$mixed_easy <- vars$mixed & vars$easy
vars$mixed_difficult <- vars$mixed & vars$difficult
vars$mixed_common <- vars$mixed & vars$common
```

### Create Variable for Distractor Analysis

For distractor analysis, a logical variable is required that identifies
all unscored multiple-choice items. In our example, it is called
`distan`.

`{r} vars$distan <- vars$raw & vars$type == "MC"}`

### Create Variables for Scores and SUF

For the calculation of sum scores and metacognition scores, as well as
for the creation of the SUF, the logical variable `suf` is required in
the dataset `vars`. This variable indicates which items were used in the
test and should be included in the SUF. These are scored dichotomous and
polytomous items without collapsed response categories.

```{r}
vars$suf <- vars$mixed
vars$suf[vars$item %in% original_items] <- TRUE
vars$suf[vars$item %in% collapsed_items] <- FALSE
vars$item[vars$suf]
```

If the scores are to be calculated separately for different groups
(e.g., test booklets), an additional logical variable analogous to `suf`
must be created for each group, identifying all items of that group
required for the scores and the SUF. For an easy and a difficult test
booklet, the variables could, for example, be called `suf_easy` and
`suf_difficult`.

```{r}
vars$suf_easy <- ifelse(vars$suf & vars$easy, TRUE, FALSE)
vars$suf_difficult <- ifelse(vars$suf & vars$difficult, TRUE, FALSE)
```

For the calculation of sum scores and metacognition scores, a variable
(e.g., `num_cat`) is required in `vars` that contains the maximum number
of correct responses per item. For polytomous items, this corresponds to
the number of subitems, whereas for dichotomous items it is 1. The
function `calculate_num_cat()` computes the maximum number of correct
responses per item. It requires the following arguments: on the one
hand, the list `poly_items` created earlier, and on the other hand, the
name of the logical variable in `vars` that identifies all items used
for creating the scores and included in the SUF (e.g., `suf`). If the
test contains only dichotomous variables, the argument `poly_items` is
omitted.

```{r}
vars$num_cat <- NEPSroutines::calculate_num_cat(
  vars, 
  poly_items = poly_items,  
  select_suf = "suf"
)
```

### Additional Required Variables

Depending on the study design, additional variables may be required, for
example for linking. Functions for these variables are not yet
available, so they must be created manually.

### Problem with Variables of Type `haven_labelled`

Unfortunately, R Markdown currently (as of October 2024) does not always
handle variables of type `haven_labelled` correctly. This can lead to
errors during rendering that do not occur when executing the code
outside of R Markdown (e.g., the error message "invalid argument type").
In such cases, the variables must be converted without losing the UDMVs.
In most cases, the following code works, but be sure to verify afterward
that the missing values have not been converted to `NA`s.

`{r} # Convert “haven_labelled” variables to “double” resp <- haven::zap_labels(resp)  # Check whether the user-defined missing values still exist table(unlist(resp[ , vars$item]), useNA = "ifany")}`

## Check Data Structure

Once data preparation has been completed, the data structure can be
checked using several functions. Although these checks are also
performed automatically within the functions of the individual scaling
steps, conducting them in advance can save a considerable amount of
post-processing. The following functions are available for checking the
data structure:

| Function | Usage |
|----------------|--------------------------------------------------------|
| `check_logicals` | Checks the specified variables in the defined dataset for existence, logical data type, and absence of missing values. The function takes the arguments `df` (the data.frame), `name_df` (name of the data.frame as a string), and `logicals` (character vector containing the names of the variables to be checked). |
| `check_numerics` | Checks the specified variables in the defined dataset for existence, numeric data type, and, if required, for the absence of negative values and/or values greater than 1 (for dichotomous variables). The function takes the arguments `df`, `name_df`, `numerics` (character vector containing the names of the variables to be checked), `check_invalid` (logical, whether to check for negative values; default is `FALSE`), and `dich` (logical, whether to check for values greater than 1; default is `FALSE`). |
| `check_variables` | Basic function for variables of any data type. It checks the specified variables in the defined dataset only for existence. The function takes the arguments `df`, `name_df`, and `variables` (character vector containing the names of the variables to be checked). |
| `check_pid` | Checks whether duplicates exist in the ID variable (`ID_t`). |
| `check_items` | Checks whether item names are duplicated in the data.frame `vars`. |

Note that if the data structure is correct, none of the functions will
produce any output. Therefore, if no error messages appear after running
the functions, everything is set up correctly.

A data structure check could, for example, look as follows:

```{r}
# Check vars
NEPSroutines::check_items(vars$item)
NEPSroutines::check_variables(
  vars, "vars", c("item", "type", "correct_response")
)
NEPSroutines::check_logicals(
  vars, "vars", c("raw", "dich", "poly", "mixed", "easy", "difficult")
)
NEPSroutines::check_numerics(
  vars, "vars", c("scoring", "position_easy", "position_difficult")
)

# Check resp
NEPSroutines::check_variables(resp, "resp", c("ID_t", vars$item[vars$raw])) NEPSroutines::check_logicals(resp, "resp", c("valid", "easy", "difficult")) NEPSroutines::check_numerics(
  resp, "resp", c("sex", "migration", "books"), dich = TRUE, check_invalid = TRUE
)
NEPSroutines::check_numerics(resp, "resp", vars$item[vars$dich], dich = TRUE)
NEPSroutines::check_numerics(resp, "resp", vars$item[vars$poly])
NEPSroutines::check_pid(resp$ID_t)
```

## Save Data

Once the preparations have been completed, the data can be saved.

```{r}
save(resp, vars, mvs, labels_mvs, file = "data/dat.Rdata")
```

From this point onward, the data preparation step can be skipped, and
the prepared data can be loaded directly.

```{r}
load("data/dat.Rdata")
```

## Changes to Items During Scaling

It is common for the item set used in the analyses to change during the
scaling process, for example because individual items are excluded due
to poor item statistics or because multiple items are combined into a
new item. In such cases, certain parts of the data preparation must be
repeated, such as creating new variables to identify the final item set
and the final item positions, or modifying existing variables such as
the scoring variable or the validity variable accordingly.
