---
title: "Example Scaling Script for dat4"
author: "Jana Welling"
date: "`r Sys.time()`"
output:
    html_document:
        toc: true
        number_sections: true
        toc_float: true
        theme: readable
        highlight: tango
        df_print: paged
        code_folding: show
editor_options: 
  chunk_output_type: console
---

# Preparation of R and data

## Load package and example data

```{r load, message = FALSE}

library("NEPSroutines")

data("dat4")
resp <- dat4$resp
vars <- dat4$vars

```

## User-defined missing values

```{r user-defined missing values}

table(unlist(resp[vars$item]))

mvs = c(
  OM = -97,
  NV = -95,
  NR = -94,
  NP = -56,
  ND = -55,
  MD = -54
)

labels_mvs = c(
  ALL = "total missing items",
  OM = "omitted items",
  NV = "not valid items",
  NR = "not reached items",
  NP = "not participated",
  ND = "not determinable items",
  MD = "items missing by design"
)

```

## Attributes for socio-demographic variables

```{r attributes}

# Sex
attributes(resp$sex)$labels <- c(
  female = 0,
  male = 1
)

# Books
attributes(resp$books)$labels <- c(
  less_than_100 = 0,
  more_than_100 = 1
)

```


# Sample and Booklet Descriptives

```{r descriptives}

# Sample size with only valid cases
NEPSroutines::n_valid(resp, valid = "valid")

# Descriptives (mean, sd, etc.) of continuous variables
NEPSroutines::desc_con(resp, desc = "age", valid = "valid")

# Descriptives (attributes, frequency) of nominal socio-demographic variables
NEPSroutines::show_attributes(resp, desc = c("sex", "books"))
NEPSroutines::desc_nom(resp, desc = c("sex", "books"), valid = "valid")

```


# Missing Responses Analyses

## Missing Responses by Person

```{r missing responses by person}

max(vars$pos[vars$stage1])
max(vars$pos[vars$stage2])
max(vars$pos[vars$stage3])

NEPSroutines::mv_person(
  resp = resp,
  vars = vars,
  select = "mixed",
  valid = "valid",
  stages = c(stage1 = 6, stage2 = 12, stage3 = 18),
  mvs = mvs,
  labels_mvs = labels_mvs,
  missing_by_design = c(-54,-56),
  show_all = TRUE,
  overwrite = TRUE,
  plots = TRUE,
  save = TRUE,
  print = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables",
  path_plots = "plots/missings_by_person",
  digits = 2,
  warn = TRUE,
  verbose = FALSE
)

```

## Missing Responses by Item

```{r missing responses by item}

resp$stage1 <- rowSums(resp[,vars$item[vars$stage1 & !vars$raw]] >= 0) > 0
resp$stage2 <- rowSums(resp[,vars$item[vars$stage2 & !vars$raw]] >= 0) > 0
resp$stage3 <- rowSums(resp[,vars$item[vars$stage3 & !vars$raw]] >= 0) > 0
table(resp$stage2,resp$stage3)

NEPSroutines::mv_item(
  resp = resp,
  vars = vars,
  select = "mixed",
  valid = "valid",
  position = "pos",
  stages = c("stage1", "stage2", "stage3"),
  mvs = mvs,
  labels_mvs = labels_mvs,
  missing_by_design = c(-54,-56),
  overwrite = TRUE,
  plots = TRUE,
  save = TRUE,
  print = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables",
  path_plots = "plots/missings_by_item",
  digits = 2,
  warn = TRUE,
  verbose = FALSE
)

```


# IRT Analyses

## Dichotomous items

```{r IRT analysis with dichotomous items}

NEPSroutines::irt_analysis(
  resp = resp,
  vars = vars,
  select = "dich",
  valid = "valid",
  mvs = mvs,
  plots = TRUE,
  save = TRUE,
  print = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables",
  path_plots = "plots",
  overwrite = TRUE,
  digits = 2,
  verbose = FALSE
)

```

## All items

```{r IRT analysis with all items}

NEPSroutines::irt_analysis(
  resp = resp,
  vars = vars,
  select = "mixed",
  valid = "valid",
  scoring = "scoring",
  mvs = mvs,
  plots = TRUE,
  save = TRUE,
  print = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables",
  path_plots = "plots",
  overwrite = TRUE,
  digits = 2,
  verbose = FALSE
)

```


# DIF Analysis

## Dichotomous items

```{r dif analysis for dichotomous items}

NEPSroutines::dif_analysis(
  resp = resp,
  vars = vars,
  select = "dich",
  valid = "valid",
  dif_vars = c("sex", "books"),
  mvs = mvs,
  overwrite = TRUE,
  verbose = FALSE,
  save = TRUE,
  print = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables"
)

```

## All items

```{r dif analysis for all items}

NEPSroutines::dif_analysis(
  resp = resp,
  vars = vars,
  select = "mixed",
  valid = "valid",
  dif_vars = c("sex", "books"),
  scoring = "scoring",
  mvs = mvs,
  control = list(
    Msteps = 6,
    maxiter = 5000
  ),
  overwrite = TRUE,
  verbose = FALSE,
  save = TRUE,
  print = TRUE,
  return = FALSE,
  path_results = "results",
  path_table = "tables"
)

```


# Distractor Analysis

```{r distractor analysis}

NEPSroutines::dis_analysis(
  resp = resp,
  vars = vars,
  valid = "valid",
  select_raw = "raw",
  correct = "correct",
  mvs = mvs,
  print = TRUE,
  save = TRUE,
  overwrite = TRUE,
  path_results = "results",
  path_table = "tables"
)

```


# Dimensionality Analysis

```{r dimensionality analysis}

# Create numerical dimensionality variable
vars$component_num <- as.numeric(as.factor(vars$component))
table(vars$component, vars$component_num)

# Conduct dimensionality analysis
NEPSroutines::dim_analysis(
  resp = resp,
  vars = vars,
  select = "mixed",
  valid = "valid",
  scoring = "scoring",
  irtmodel = "PCM2",
  dim = "component_num",
  mvs = mvs,
  return = FALSE,
  save = TRUE,
  print = TRUE,
  path_table = "tables", 
  path_results = "results",
  overwrite = TRUE,
  verbose = FALSE
)

```


# Create Scores and SUF

```{r suf}

scores <- NEPSroutines::create_scores(
  resp,
  vars,
  score_name = "sca14",
  select = "mixed",
  valid = "valid",
  scoring = "scoring",
  mvs = mvs,
  wle = TRUE,
  sum_score = TRUE,
  sum_select = "dich",
  metap = FALSE,
  return = TRUE,
  save = TRUE,
  overwrite = TRUE,
  path_results = "results"
)

NEPSroutines::create_suf(
  resp,
  vars,
  select = "mixed",
  competence = "Science",
  scores = scores,
  score_name = "sca14",
  return = FALSE,
  path = "suf"
)

rm(scores)

```


# Session

```{r session-info}
sessionInfo()
```
